### 2025-01-26 SI.tex
update on mac 2025-01-26

\documentclass[preprint,review,12pt,authoryear]{elsarticle}

\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{titlesec} % 用于自定义章节标题样式
\usepackage{caption}
\usepackage{tabularx}
\usepackage{booktabs}
\renewcommand{\thesection}{S\arabic{section}}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}

\begin{document}
\captionsetup[figure]{name={\textbf{Fig S}},labelsep=period} 
\captionsetup[table]{name={Table S},labelsep=period}
% \captionsetup[table]{
%   name={Table S},
%   labelformat=simple, % 使用简单的编号格式
%   labelsep=space,     % 编号和标题之间的分隔符为一个空格
%   justification=centering, % 居中对齐
% }

\begin{center}
\Large 
Supplementary information for 'Inverse design workflow of implicit surface-based cellular materials via conditional generative model and active learning'
\end{center}

\begin{center}
    Jiaxuan Ma, Bin Cao, Yuan Tian$^*$, Sheng Sun$^*$
\end{center}

%% \linenumbers
\section{Mechanical Property of TPMS}

\begin{figure}
    \centering
    \includegraphics[width=1\linewidth]{figures/S1.pdf}
    \caption{Voxelization of a TPMS-based unit cell (\textbf{a}) and 3D visualization of effective elastic tensor (\textbf{b})}
    \label{fig:s1}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=1\linewidth]{figures/S2.pdf}
    \caption{The relationship between effective elastic modulus E, Possion's ration $v$ and relative density $\rho$.}
    \label{fig:s2}
\end{figure}

The voxelization of a TPMS-based unit cell and 3D visualization of effective elastic tensor obtianed by numerical homogenization method are shown in Fig S\ref{fig:s1}
In regions of low density, specifically when the relative density is below 0.2, the distribution of the elastic modulus is mixed. However, when the relative density exceeds 0.2, the relationship between the elastic modulus and relative density in hybrid structures bifurcates into two distinct categories. One trend aligns with the structure G, while the other aligns with the structure D. This division is illustrated by the fitted curves, depicted as black dashed lines (see Fig S\ref{fig:s2}). The corresponding fitted formulas are as follows:
\begin{equation}
    E_G = E_s\rho^{2.26}
\end{equation}
\begin{equation}
    E_D = E_s\rho^{2.42}
\end{equation}
where $E_s$ is the elastic modulus of Ti6Al4V.

The Ti6Al4V material has an elastic modulus of 46,532.9 MPa and a Poisson's ratio of 0.34. The plastic constitutive law is detailed in Table S\ref{tab:s1}\citep{Peng2023}.

\begin{table}
\centering
\caption{~Plastic constituent law of Ti6Al4V\citep{Peng2023}}
\begin{tabularx}{0.8\textwidth}{XX}
\toprule
Stress (MPa) & Plastic strain \\
\midrule
919.9167 & 0.000000000 \\
986.4167 & 0.010345953 \\
1041.8333 & 0.019444969 \\
1086.1667 & 0.028543986 \\
1119.4167 & 0.037643003 \\
1141.5833 & 0.046742019 \\
1139.3667 & 0.055841036 \\
1137.1500 & 0.064940052 \\
1131.6083 & 0.074039069 \\
1124.9583 & 0.083138085 \\
1116.0917 & 0.092237102 \\
1108.3333 & 0.101336118 \\
1075.0833 & 0.110435135 \\
1030.7500 & 0.119534152 \\
980.8750 & 0.128633168 \\
908.8333 & 0.137732185 \\
831.2500 & 0.146831201 \\
\bottomrule
\end{tabularx}
\label{tab:s1}
\end{table}

\section{Expected Improvement (EI)}
Expected Improvement (EI) is a widely used acquisition function in Bayesian optimization, which measures the expected improvement over the current best-known solution.

Assume we have observed a dataset $\mathcal{D}_n=\{x_{1:n},f_{1:n}\}$, where $f(x_i)$ represents the function value at point $x_i$. The current best-known value is $f^*_n=\max\{f_1,...,f_n\}$.

For a new point $x_{n+1}$ with function value $f_{n+1}$, the improvement is defined as:
\begin{equation}
    I(x_{n+1})=\max(f_{n+1}-f^*_n,0)
\end{equation}
This means improvement is only considered if $f_{n+1}$ exceeds the current best value $f^*_n$.

The Expected Improvement $\alpha_{\text{EI}}(x)$ is the expected value of the improvement $I_{\text{EI}}(x)$:
\begin{equation}
\alpha_{\text{EI}}(x)=\mathbb{E}[I_\text{EI}(x)|\mathcal{D}]=\mathbb{E}[\max(f_{n+1}-f^*_n,0)]
\end{equation}
Assuming the objective function $f(x)$ follows a Gaussian process, the predicted value $f_{N+1}$ at point $x$ follows a normal distribution $\mathcal{N}(\mu(x), \Sigma^2(x))$, where $\mu(x)$ and $\Sigma(x)$ are the posterior mean and standard deviation, respectively.

Thus, we have 
\begin{equation}
\alpha_{\text{EI}}(x)=\int_{-\infty}^{\infty}\max(f_{n+1}-f^*_n,0)\cdot p(f_{n+1}|x)df_{n+1}
\end{equation}
Since max($f_{n+1}-f^*_n, 0$) is zero when $f_{n+1}<f^*_n$, the integral can be simplified to:
\begin{equation}
  \alpha_{\text{EI}}(x)= \int_{f^*_n}^\infty(f_{n+1}-f^*_n)\cdot p(f_{n+1}|x)df_{n+1}
\end{equation}
\textbf{Reparametrization trick}

Let $z=\frac{f_{n+1}-\mu(x)}{\sigma(x)}$,  so $f_{n+1}=\mu(x)+\sigma(x)z$, and $p(f_{n+1}|x)$ becomes the standard normal density function $\phi(z)$. Therefore:

\begin{equation}
\begin{aligned}
  \alpha_{\text{EI}}(x)&=\int_{\frac{f^*_n-\mu(x)}{\sigma(x)}}^\infty(\mu(x)+\sigma(x)z -f^*_n)\cdot\phi(z)dz\\
    &=(\mu(x)-f^*_n)\int^\infty_{\frac{f^*_n-\mu(x)}{\sigma(x)}}\phi(z)dz + \sigma(x)\int^\infty_\frac{f_n^*-\mu(x)}{\sigma(x)}z\cdot \phi(z)dz
 \end{aligned}
\end{equation}
Using the properties of the standard normal distribution:
\begin{equation}
    \int_a^\infty z\cdot\phi(z)dz=-\phi(a)
\end{equation}
\begin{equation}
    \int_a^\infty\phi(z) dz = 1-\Phi(a)
\end{equation}
where $\phi (z)$ is the standard normal density function and $\Phi(z)$ is the standard normal cumulative distribution function.
Thus:
\begin{equation}
\begin{aligned}
  \alpha_{\text{EI}}(x)&=(\mu(x)-f^*_n)[1-\Phi(\frac{f^*_n-\mu(x)}{\Sigma(x)})]+\Sigma(x)\phi(\frac{f^*_n-\mu(x)}{\Sigma(x)}) \\
  &=(\mu(x)-f^*_n)\Phi(\frac{\mu(x)-f^*_n}{\Sigma(x)}) + \Sigma(x)\phi(\frac{\mu(x)-f^*_n}{\Sigma(x)}) \\
\end{aligned}
\end{equation}

\section{Toy Problem for Constraint-aware Active Learning}
The unconstrained objective function is defined as:
\begin{equation}
    f(x) = 0.001\cos(0.5x) + \frac{x}{30} + \sin(0.6x), \quad x \in [0, 17]
\end{equation}

The constraint function is given by:
\begin{equation}
c(x) = \frac{1}{1+e^{(x-8.5)}}, \quad x \in [0, 17]
\end{equation}

Consequently, the objective function incorporating the constraint can be expressed as:
\begin{equation}
f_c(x) = f(x) \cdot c(x), \quad x \in [0, 17]
\end{equation}
The maximum value of the unconstrained objective function, \( f(x) \), occurs at \( x = 13 \), whereas the maximum value of the constrained objective function, \( f_c(x) \), is located at \( x = 2.5 \). To model these functions, two Gaussian process regressions are employed. In Bayesian Global Optimization (BGO), an optimizer is used to search for a promising point \(\hat{x}\) by maximizing an infill criterion with respect to surrogate models, rather than relying on the 'true' objective functions. The constraint function applied to the objective function can similarly be applied to the infill criterion, or acquisition function.

The EI score and the constraint-aware EI score are derived from \(\alpha_{\text{EI}} = \mathbb{E}(I_{\text{EI}}(x))\) and \(\alpha_{\text{EI-C}} = \mathbb{E}(I_{\text{EI-C}}(x)) = \alpha_{\text{EI}}(x) \cdot c(x)\), respectively. The query point recommended by \(\alpha_{\text{EI-C}}\) achieve the optimal value in the constrained objective function \( f_c(x) \).

\section{Feature Normalization}

The structural parameters $\alpha_1$ and $\alpha_2$ of the TPMS are normalized before  being input to neural network, along with their geometric and property characteristics, such as relative density $\rho$, thickness $th$, pore diameter $d$, and effective modulus $E$. This normalization is achieved using the following equation:

\begin{equation}
(\hat{\cdot}) = 2 \times \frac{(\cdot) - \min(\cdot)}{\max(\cdot) - \min(\cdot)} - 1  
\end{equation}

\begin{table}
    \centering
        \caption{The hyper-parameters and architecture of TPMS-GAN($G_\phi^1$) }
    \begin{tabular}{|c|c|c|c|} \hline  
         Batch size&  23&  Learning rate& 0.0002\\ \hline  
         Epochs&  2000&  Latent space& 3\\ \hline  
         Input size&  4&  \textbf{Condition size}& 1\\ \hline
 $\lambda_{gp}$& 10& $\eta$&0.5\\\hline \hline  
 \multicolumn{4}{|c|}{Hidden layer of generator: 128, 256, 512, 1024}\\ \hline  
 \multicolumn{4}{|c|}{Hidden layers of discriminator: 1024, 512, 256, 128}\\ \hline  
 \multicolumn{4}{|c|}{Hidden layers of navigator: 1024, 512, 128}\\ \hline 
    \end{tabular}
    \label{tab:s2}
\end{table}

\begin{table}
    \centering
        \caption{The hyper-parameters and architecture of TPMS-GAN($G_\phi^2$) }
    \begin{tabular}{|c|c|c|c|} \hline  
         Batch size&  23&  Learning rate& 0.0002\\ \hline  
         Epochs&  2000&  Latent space& 3\\ \hline  
         Input size&  4&  \textbf{Condition size}& 3\\ \hline
 $\lambda_{gp}$& 10& $\eta$&0.5\\\hline \hline  
 \multicolumn{4}{|c|}{Hidden layer of generator: 128, 256, 512, 1024}\\ \hline  
 \multicolumn{4}{|c|}{Hidden layers of discriminator: 1024, 512, 256, 128}\\ \hline  
 \multicolumn{4}{|c|}{Hidden layers of navigator: 1024, 512, 128}\\ \hline 
    \end{tabular}
    \label{tab:s3}
\end{table}

\begin{table}
    \centering
        \caption{The hyper-parameters and architecture of ITPMS-GAN($IG_\psi$) }
    \begin{tabular}{|c|c|c|c|} \hline  
         Batch size&  23&  Learning rate& 0.0002\\ \hline  
         Epochs&  2000&  Input size & 4\\ \hline  
         Output size&  3& Hidden size & 1024, 512, 128\\ \hline

    \end{tabular}
    \label{tab:s4}
\end{table}

\section{ML surrogte model}

For evaluating the effective elastic modulus \(E\) of the TPMS unit generated by TPMS-GAN (\(G_\phi^1\)) convinecely, a surrogate model was developed by comparing five machine learning models: linear regression, decision tree regression, random forest, support vector machine, and Gradient boost regression. Figure \ref{fig:s3} illustrates the mean and variance of the \(R^2\) values for these models, obtained through a 10-fold cross-validation method. Among the models evaluated, the random forest model demonstrated superior performance, achieving an \(R^2\) value of 0.976 with a variance of 0.0045.

\begin{figure}
    \centering
    \includegraphics[width=0.5\linewidth]{figures/S3.pdf}
    \caption{Comparison of 10-fold $R^2$ of ML models}
    \label{fig:s3}
\end{figure}

\section{Computing Platform}
The neural network models training are performed in PyTorch on a laptop with 64 GB RAM and an Nvidia GeForce RTX 2060S GPU. The numerical homogenization method and COMSOL software are executed on a laptop with an Intel Core i7-10875H CPU featuring 8 cores.

%% If you have bibdatabase file and want bibtex to generate the
%% bibitems, please use
%%
\bibliographystyle{elsarticle-harv} 
\bibliography{refs}

%% else use the following coding to input the bibitems directly in the
%% TeX file.

% \begin{thebibliography}{00}

% %% \bibitem[Author(year)]{label}
% %% Text of bibliographic item

% \bibitem[ ()]{}

% \end{thebibliography}
\end{document}

\endinput
%%
%% End of file `elsarticle-template-harv.tex'.

### 2025-01-26 manuscript.tex
update on mac 2025-01-26

%% 
%% Copyright 2007-2020 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%% 
%% Template article for Elsevier's document class `elsarticle'
%% with harvard style bibliographic references

\documentclass[preprint,review,12pt,authoryear]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times,authoryear]{elsarticle}
%% \documentclass[final,1p,times,twocolumn,authoryear]{elsarticle}
%% \documentclass[final,3p,times,authoryear]{elsarticle}
%% \documentclass[final,3p,times,twocolumn,authoryear]{elsarticle}
%% \documentclass[final,5p,times,authoryear]{elsarticle}
%% \documentclass[final,5p,times,twocolumn,authoryear]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage {caption}
% \renewcommand{\figurename}{\textbf{Fig}}
% \captionsetup[figure]{labelsep=period}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}

\journal{Journal of the Mechanics and Physics of Solids}

\begin{document}
\captionsetup[figure]{name={\textbf{Fig.}},labelsep=period}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \affiliation for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \affiliation{organization={},
%%            addressline={}, 
%%            city={},
%%            postcode={}, 
%%            state={},
%%            country={}}
%% \fntext[label3]{}

\title{Inverse design workflow of implicit surface-based cellular materials via conditional generative model and active Learning}

\author[1]{Jiaxuan Ma}
\author[3]{Bin Cao}
\author[1]{Yuan Tian, \corref{cor1}}
\ead{tian0321@shu.edu.cn}
\author[1,2]{Sheng Sun, \corref{cor1}}
\ead{mgissh@t.shu.edu.cn}

\address[1]{Materials Genome Institute, Shanghai University, Shanghai, 200444, China}
\address[2]{Shanghai Frontier Science Center of Mechanoinformatics, Shanghai University, Shanghai, 200444, China}
\address[3]{Advanced Materials Thrust, Hong Kong University of Science and Technology (Guangzhou), Guangzhou, 511400, Guangdong, China}

\cortext[cor1]{Corresponding author}

\begin{abstract}
Implicit surface-based cellular materials have gained widespread adoption in bone scaffolds applications due to their similarities to bone structure. These materials excel in providing good mechanical properties and bioadaptability, creating suitable conditions for bone tissue regeneration. However, the rational design of these materials typically depends on prior knowledge of experts and requires large of  trail-and-error experiments. Here, we present a data-efficient two-stage bi-objective optimization method within a machine learning framework that considers the varying costs associated different objectives. Specifically, we employ this methodology to orthopedic implant inverse design, integrating generative model, active leaning, and finite element analysis to achieve both biocompatible elastic modulus and higher yield strength cellular materials. Our approach demonstrates remarkable improvements in overall performance compared to initial datasets, while simultaneously reducing about sixfold design cost relative to one-step bi-objective optimization machine learning method. This methodology establishes an efficient paradigm for the rapid and intelligent design of cellular materials with tailored mechanical properties, particularly valuable in scenarios involving objectives with unbalanced computational costs.
\end{abstract}

%%Graphical abstract
\begin{graphicalabstract}
%\includegraphics{grabs}
\end{graphicalabstract}

%%Research highlights
\begin{highlights}
\item Developing TPMS-GAN with navigator was proposed to generate TMPS unit cell under desired conditions of mechanical properties and geometries.
\item Developing Inversed TPMS-GAN to design TPMS unit cell in geomety feature in a explainable way instead of through latent space or coefficients of implicit function 
\item Proposing a constraint-aware active learning method to address bi-objective optimization problem with unbalanced costs of objective function. 
\end{highlights}

\begin{keyword}

Multi-objective optimization \sep Cellular structure design \sep Generative adversarial network \sep Constraint-aware active learning
\end{keyword}

\end{frontmatter}

%% \linenumbers

%% main text
\section{Introduction}
Cellular materials are one of the most widely adopted engineering materials due to their excellent mechanical performance and adaptable properties, such as lightweight structures \citep{Schaedler2011, Berger2017, Han2015, Tancogne-Dejean2018}, thermal insulation \citep{Li2021d}, acoustic \citep{Sekar2024} and tissue engineering \citep{Li2024c,Peng2023,Tabrizian2024}. Moreover,  recent progress in additive manufacturing (AM) has further enabled the inexpensive and tailored fabrication of complex structures. Despite the broad applicability and immense potential of cellular materials, designing them is particularly difficult.

The traditional approach to design often relies on nature-inspired structures \citep{Fernandes2021,Bandyopadhyay2021,Sethi2023}, human intuition \citep{Schaedler2011,Berger2017,Xu2016a}, and numerical simulations, including topology optimization \citep{Andersen2019,Bendsoe1999,Collet2018}, spinodal separation \citep{Hsieh2019,Roding2022}, or Gaussian random fields \citep{Kumar2020,Zheng2020abc}. These rule-based methods are typically exhausting and time-consuming. Furthermore, the performance of resultant designs is highly dependent on the professional expertise of the designer.

With the rapid development of artificial intelligence (AI), machine learning has significantly transformed the design paradigm of cellular materials. By learning from data, machine learning models can effectively capture the non-linear relationships between geometric features and mechanical properties of cellular materials. Once trained, these models offer a low-cost inference capability, serving as surrogates for expensive numerical simulations and experiments. Consequently, machine learning models can be seamlessly integrated into heuristic algorithms facilitating the optimization of cellular material structures with target mechanical properties, such as elastic modulus \citep{Garland2021,Lee2022,Chen2024b}, bulk resistance \citep{Liu2020a}, and stress-strain curve \citep{Deng2022a,Ma2020b}.  However, surrogate optimization is a high-throughput selection process that necessitates multiple invocations of machine learning models, presenting challenges for global optimization problems and real-time design requirements.

Generative models, such as variational auto-encoder (VAE) \citep{Wang2020a,Zheng2023},  generative adversarial network (GAN) \citep{Nie2020, Shen2022,Kim2020b} and diffusion model \citep{Bastek2023,Maze2022,Vlassis2023}, have demonstrated significant capabilities in cellular materials design. These models can learn the distribution of structures of training dataset and sample new structures from it. In particular, conditional generative models can produce novel structures with a target property, making them suitable for inverse design problems in cellular materials where multiple structures correspond to a single property. Although generative models have been widely used in designing cellular materials, the cost of building dataset has rarely been considered, especially in multi-objective problems. It is common to encounter the scenario where one objective function is inexpensive while another is costly. This is particularly prevalent in design of cellular structures, where linear and nonlinear mechanical properties must be considered simultaneously.

Triply periodic minimal surfaces (TPMS) are a family of cellular materials based on implicit functions, and the shapes of the unit cells can be controlled by adjusting the coefficients of the implicit function and the constants of the level set \citep{Ma2020a}. TPMS are characterized by their locally symmetric saddles shapes with vanishing mean curvature and non-positive Gaussian curvature. Each domain of TPMS is a single, connected, infinite component without sealed cavities in its geometry \citep{Kapfer2011}. These structures are particularly valuable in orthopedic implants due to their ability to mimic the diverse characteristics of bone. For such applications, it is crucial that the elastic module of the implant matches that of human bone to minimize stress shielding, while the yield stress should be as high as possible to provide adequate mechanical support and a long fatigue life. The elastic modulus of TPMS unit cell can be readily evaluated using numerical homogenization methods. However, the evaluation of yield stress incurs significant costs due to the nonlinear plasticity constitute of base materials via finite element method (FEM).

In the work, we propose a two-step strategy that integrates generative model with active learning algorithms to address bi-objective design problem of TPMS unit cells associated with imbalanced costs of properties. As demonstrated in Fig \ref{fig:1}, our approach consists of three main parts: (1) generate structures with a desired elastic modulus. In this step, a TPMS-GAN model is trained on a dataset containing TPMS unit cells and their corresponding elastic modulus. Then the generator of the TPMS-GAN produces structures with target elastic modulus, forming a virtual structure space (VSS). (2) inversed TPMS-GAN (ITPMS-GAN) model was developed to explore the latent space of TPMS-GAN, allowing for direct geometric manipulation of TPMS structures instead of modifying implicit function parameters. (3) an elastic modulus constraint-aware active learning approach for yield strength optimization. Initially, the yield strength of a select number of TPMS structures within VSS are evaluated to establish the initial dataset via FEM. Subsequently, elastic modulus constraint-aware active learning based on Bayesian optimization (BO) is employed to optimize the yield strength of TPMS unit cells. BO method has been proven significant efficiency in materials design with small data \citep{Ma2024b,Cao2024a,Tian2024a}.

\begin{figure}
    \centering
    \includegraphics[width=1\linewidth]{figures/1.pdf}
    \caption{\textbf{An overview of the proposed workflow for TPMS unit cells design.} \textbf{a} The generator in TPMS-GAN model produces virtual design space ($\Omega_E$) with desired elastic modulus. \textbf{b} The ITPMS-GAN model was developed to edit the TPMS structure through geometry features to rich diversity of candidates in $\Omega_E$. \textbf{c} The machine learning (ML) algorithm interactively queries the FEM to discovery new TPMS designs with high yield strength and target elastic modulus through constrained active learning in $\Omega_E$.}
    \label{fig:1}
\end{figure}

\section{Models and methods}

\subsection{TPMS-based cellular structures}

TPMS can be produced by a simple level-set approximation equation from a sum defined in terms of the Fourier series \citep{Gandy2001,Al-Ketan2019}:
\begin{equation}
 \Psi(\boldsymbol{r})=\sum_kF(\boldsymbol{k})\text{cos}([2\pi \boldsymbol{k}\cdot \boldsymbol{r}-\alpha(\boldsymbol{k})])=0
\label{eq:1}
\end{equation}
where $\boldsymbol{k}$ is the reciprocal vector, $\alpha(\boldsymbol{k})$ is a phase shift, and the structure $F(\boldsymbol{k})$ is an amplitude associated with the given $\boldsymbol{k}$ vector. Truncating the series to the leading term gives rise to a function $\phi$ that consists of a combination of trigonometric functions and satisfies the equality $\phi(x,y,z)=c$. The function $\phi(x, y, z)$ defines a surface evaluated at the isovalue (i.e., level-set constant) $c$ and has a topology similar to that of a minimal surface.

\subsection{Effective properties of homogenized cellular structures}
\label{subsec:homo}

In the work, a voxel-based asymptotic homogenization method \citep{Dong2019} is employed to calculate the effective elastic tensor of TPMS unit cells. The asymptotic homogenization method posits that physical quantities such as stress and strain depend on both the macroscale ($X$) and the microscale ($x/\varepsilon$), where $\varepsilon$ is the scale factor. These quantities are homogenized at the macroscale and exhibit periodicity at the microscale. The microscopic strain tensor can be asymptotically expanded, and by neglecting higher-order terms, it can be expressed as:
\begin{equation}
    \varepsilon = \bar{\varepsilon} + \varepsilon^{*}
\label{eq:2}
\end{equation}
Here, $\bar{\varepsilon}$ represents the mean or macroscopic strain within the unit cell, while $\varepsilon^{*}$ denotes the perturbation strain at the periodic microscale. The perturbation strain is derived from the mechanical balance equation:
\begin{equation}
\int_{\Omega}\hat{\varepsilon}^T:\mathbb{C}:\varepsilon^{*}d\Omega = \int_{\Omega}\hat{\varepsilon}^T:\mathbb{C}:\bar{\varepsilon}
\label{eq:3}
\end{equation}
In this equation, $\hat{\varepsilon}$ is the virtual strain, $\mathbb{C}$ is the elastic tensor of the constituent materials, and $\Omega$ represents the unit cell. This equation is numerically discretized and evaluated using the FEM, which employs eight-node hexahedrons to voxelize each unit cell into $40 \times 40 \times 40$ cubes (more details are provided in Supplement S1). Once $\varepsilon^{*}$ is obtained, the effective elastic tensor $\mathbb{C}^H$ can be determined using the following equation:
\begin{equation}
\mathbb{C}^H:\bar{\varepsilon} = \frac{1}{|\Omega|}\int_{\Omega}\mathbb{C}:(\bar{\varepsilon}+\varepsilon^{*})d\Omega
    \label{eq:4}
\end{equation}
where $|\Omega|$ denotes the volume of the unit cell.

From the effective elastic tensor $\mathbb{C}^H$, the compliance tensor $\mathbb{S}^H$ can be derived, and its Voigt form is expressed as:
\begin{equation}
\mathbb{S}^H = \begin{bmatrix}
\frac{1}{E_x} & -\frac{v_{yx}}{E_y} & -\frac{v_{zx}}{E_z} & 0 & 0 & 0 \\
-\frac{v_{xy}}{E_x} & \frac{1}{E_y} & -\frac{v_{zy}}{E_z} & 0 & 0 & 0 \\
-\frac{v_{xz}}{E_x} & -\frac{v_{yz}}{E_z} & \frac{1}{E_z} & 0 & 0 & 0 \\
0 & 0 & 0 & \frac{1}{G_{yz}} & 0 & 0 \\
0 & 0 & 0 & 0 & \frac{1}{G_{zx}} & 0 \\
0 & 0 & 0 & 0 & 0 & \frac{1}{G_{xy}}
\end{bmatrix}
\label{eq:5}
\end{equation}

In this matrix, $E_i$ represents the elastic modulus along the $i^{\text{th}}$ direction, where $i \in \{x, y, z\}$. In the work, for cubic symmetric unit cells, we have effective elastic module $E^H=E_x=E_y=E_z$. Additionally, elastic moduli in other directions can be obtained from $\mathbb{S}^H$ using the following equation:
\begin{equation}
\frac{1}{E_{ijk}} = \mathbb{S}^H_{11} - 2 \left(\mathbb{S}^H_{11} - \mathbb{S}^H_{12} - \frac{1}{2} \mathbb{S}^H_{44} \right) \times \left( \ell_{i1}^2 \ell_{j2}^2 + \ell_{j2}^2 \ell_{k3}^2 + \ell_{i1}^2 \ell_{k3}^2 \right)
    \label{eq:6}
\end{equation}
Here, $E_{ijk}$ is the elastic moduli along the $[i,j,k]$ direction, and $\ell$ is the cosine of the angle between the orientation $[i,j,k]$ and the coordinate axes $[x, y, z]$. This approach allows for the evaluation of elastic modulus in any orientation of the unit cell, facilitating the construction of a three-dimensional elastic modulus surface.

\subsection{The architecture of TPMS-WGAN model}

In the work, we employ a conditional Wasserstein GAN comprising four components: a generator network ($G_\phi$), a discriminator network ($D_\theta$),  a navigator network ($R_\omega$) and a condition module $\boldsymbol{C}$ that consists of mechanical properties and geometry characterization of the TPMS unit cell. Each condition can be turned on/off during the training process to meet various design requirements (see Fig.\ref{fig:3} ). The generator $G_\phi$ (with set of trainable parameters $\phi$) map the Gaussian noise ($z$) and conditions to TPMS's parameter space $\boldsymbol{p}$ in $\mathbb{R}^4$, and achieve the fake $\boldsymbol{p}'$. While the discriminator $D_\theta$ (with set of trainable parameters $\theta$) evaluate whether a given set of structure parameters are "real" or not. It takes $\boldsymbol{p},\boldsymbol{p}'$ and  $\boldsymbol{C}$ as input and its output $D_\theta(\boldsymbol{p}'|\boldsymbol{C})$ is a function value representing the degree of realism of $\boldsymbol{p}'$. During the training process, the goal of the generator $G_\phi$ is to produce structure parameters $\boldsymbol{p}'$ of TPMS that can deceive the discriminator $D_\theta$. Simultaneously, the objective of $D_\theta$ is to distinguish structures $\boldsymbol{p}'$ generated by $G_\phi(\boldsymbol{z}|\boldsymbol{C})$ and real structure $\boldsymbol{p}$. $G_\phi$ and $D_\theta$ play the following two-player minimax game with loss function:
\begin{equation}
\mathcal{L}_{(G_\phi, D_\theta)}= \min_G \max_{D} \mathbb{E}_{\boldsymbol{p} \sim \mathbb{P}_r} \left[ D_\theta(\boldsymbol{p}|\boldsymbol{C}) \right] - \mathbb{E}_{\boldsymbol{p}' \sim \mathbb{P}_g} \left[ D_\theta (\boldsymbol{p}') \right]
\label{eq:7}
\end{equation}
where $D$ belongs to the set of 1-Lipschitz functions, $\mathbb{P}_r$ and $\mathbb{P}_g$ are distribution of dataset and model distribution implicitly defined by $\boldsymbol{p}'=G_\phi(\boldsymbol{z}|\boldsymbol{C}) $, respectively. In addition, we employ the Wasserstein GAN gradient penalty (WGAN-GP) method to address the delicate and unstable training issues associated with vanishing or exploding gradients. Further details can be found in \citep{Gulrajani2017}.

\begin{figure}
    \centering
    \includegraphics[width=1\linewidth]{figures/3.pdf}        
    \caption{\textbf{Generative modeling framework}. The conditional WGAN model can address multiple conditions including property and geometry characterizations of TPMS unit cell, here we called it TPMS-WGAN. Each condition can be turned on$/$off to meet various design requirements. Considering elastic modulus, the TPMS-WGAN takes effective elastic modulus $E$ and random noise $\boldsymbol{z} (\boldsymbol{z}\sim\mathcal{N}(\mathbf{0},\mathbf{I})$,a Gaussian distribution of zero mean and the identity as the covariance matrix) as input to generator $G_\phi^1$, and the generated TPMS structure (denoted by implicit function parameters $\boldsymbol{p}'$), $E$ and the real TPMS structure (denoted by $\boldsymbol{p}$) are then passed to the discriminator $D_\theta$ to output value $f_D$. The $\boldsymbol{p}'$ also is passed navigator $R_\omega$ to obtained the predicted effective elastic modulus $E'$.}
    \label{fig:3}
\end{figure}

\subsection{Constraint-aware active learning}
\label{sec:2-4}
Active learning methods based BO are popular in addressing black-box problems that are expensive to evaluate. Unlike gradient-based and heuristic optimization techniques, which rely solely on the predicted values of surrogate models, BO utilizes the probabilistic predictions of a surrogate model that is updated sequentially. BO comprises two primary components: the surrogate model and the acquisition function (AF). Surrogate model make it possible to search the virtual design space at low computational costs with uncertainty, while AF is employed to evaluate the score of samples in a given virtual design space, considering exploration and exploitation. In the work, support vector machine (SVM) model is used to surrogates the expensive objective i.e., the FE calculation of yield stress of the TPMS unit cell. Then bootstrap method is utilized to introduce the prediction uncertainties to build the probability model $y=f(\boldsymbol{x})+\varepsilon$. The probability model is directly applied to estimate the mean value ($\mu$) and associated uncertainties ($\Sigma^2$) of candidates in a unexplored virtual design space.

BO is a sequential optimization process that explore the optimal solution through iteration. At each iteration, the SVM model is used to evaluate all the unobserved sample within virtual design space, and select the most promising candidate $\hat{\boldsymbol{x}}^*$ for simulation or experiment to obtain $f(\hat{\boldsymbol{x}}^*)$ according to AF. The obtained new data pair $(\hat{\boldsymbol{x}}^*, f(\hat{\boldsymbol{x}}^*))$ is added to the known data set $\mathcal{D} = \{(\boldsymbol{x}_1, f(\boldsymbol{x}_1)), \ldots, (\boldsymbol{x}_n, f(\boldsymbol{x}_n))\}$ and update SVM to enhance its prediction ability. The process is repeated iteratively until a predefined convergence criterion or budget is satisfied. The critical step is the selection of candidate point $\hat{\boldsymbol{x}}^*$ which is done via an AF that enables active learning of the objective $f(\cdot)$\citep{Settles2009ActiveLL}. AFs are denoted by the expected value of a user-defined utility function conditioned on the available data $\mathcal{D}$:
\begin{equation}
    \alpha(\boldsymbol{x}) = \mathbb{E}[I(\boldsymbol{x})|\mathcal{D}]
\label{eq:8}
\end{equation}
A popular utility function is expected improvement (EI) which rewards the large improvement over the best observed value $f^*$ in $\mathcal{D}$ (evaluated thus far), that is:
\begin{equation}
    I_\text{EI}(\boldsymbol{x})=\text{max}(f(\hat{\boldsymbol{x}})-f^*, 0)
    \label{eq:9}
\end{equation}
The corresponding AF can now by obtained by substituting Eq. \ref{eq:9} in Eq. \ref{eq:8} and using the reparametrization trick (more details are provided in Supplementaty S2):
\begin{equation}
\alpha_\text{EI}(\boldsymbol{x}) = \left(\mu(\boldsymbol{x}) - f^*\right) \Phi\left(\frac{\mu(\boldsymbol{x}) - f^*}{\Sigma(\boldsymbol{x})}\right) + \Sigma(\boldsymbol{x}) \phi\left(\frac{\mu(\boldsymbol{x}) - f^*}{\Sigma(\boldsymbol{x})}\right)
\label{eq:10}
\end{equation}
where $\phi(\cdot)$ is the probability density function (PDF), $\Phi(z)$ is the cumulative density function (CDF) of the standard normal random variable $z$.
The first term on the right-hand side addresses exploitation, while the second term is associated with exploration. The AF is employed to score the unknown samples in virtual design space, guiding the selection of potential candidates for next simulation or experiments.

Adding inequality constraints to BO can be formed by
\begin{equation}
\max_{c(\boldsymbol{x}) \leq \lambda} f(\boldsymbol{x})
\label{eq:11}
\end{equation}
where $c(\boldsymbol{x})$ are the other results of data set $\mathcal{D}$, and it is modeled by another probability model similar to $f(\cdot)$. The $c(\boldsymbol{x})\leq \lambda$ is a constraint function that limited the feasible area in virtual design space. The constraint-aware EI for a candidate $\hat{\boldsymbol{x}}$ can be written by:
\begin{equation}
I_{\text{EI-C}}(\hat{\boldsymbol{x}})=\Delta_\text{C}(\hat{\boldsymbol{x}})\text{max}\{0, f(\hat{\boldsymbol{x}})-f^*\}=\Delta_\text{C}(\hat{\boldsymbol{x}})I_{\text{EI}}(\hat{\boldsymbol{x}})
    \label{eq:12}
\end{equation}
where $\Delta_\text{C}(\hat{\boldsymbol{x}})\in \{0,1\}$ is a feasibility indicator function that is 1 if $c(\hat{\boldsymbol{x}})\leq \lambda$, and 0 otherwise. 
The distribution of random variable $\Delta(\hat{\boldsymbol{x}})$ is Bernoulli distribution:
\begin{equation}
    PF(\hat{\boldsymbol{x}}):=Pr[c(\boldsymbol{x})\leq \lambda] 
    \label{eq:13}
\end{equation}
The quantity $PF(\hat{\boldsymbol{x}})$ is a cumulative distribution function. These steps lead to the  constraint-aware expected improvement AF:
\begin{equation}
\begin{aligned}
\alpha_{\text{EI-C}}(\hat{\boldsymbol{x}}) &=\mathbb{E}[I_\text{EI-C}(\hat{\boldsymbol{x}})]\\
&= \mathbb{E}[\Delta_{C}(\hat{\boldsymbol{x}})I_{\text{EI}}(\hat{\boldsymbol{x}})|\hat{\boldsymbol{x}}]\\
&= \mathbb{E}[\Delta_{C}(\hat{\boldsymbol{x}})|\hat{\boldsymbol{x}}]\mathbb{E}[I_\text{EI}(\hat{\boldsymbol{x}})|\hat{\boldsymbol{x}}]\\
&=PF(\hat{\boldsymbol{x}})\alpha_{\text{EI}}(\hat{\boldsymbol{x}})
\end{aligned}
\label{eq:14}
\end{equation}
Thus $\alpha_{\text{EI-C}}(\hat{\boldsymbol{x}})$ is the a standard EI of $\hat{\boldsymbol{x}}$ over the feasible point weighted by the probability that $\hat{\boldsymbol{x}}$ is feasible. In the work, we extend the constraint-aware expected improvement AF by surrogate $PF(\hat{\boldsymbol{x}})$ with the normalized distance between the constraint value $c(\hat{\boldsymbol{x}})$ within a virtual space and a target point $c^*$. This distance is mathematically expressed as $ND(||c(\hat{\boldsymbol{x}})-c^*||)$. By incorporating the constrained function, the distribution of \(\alpha_{\text{EI}}(\hat{\boldsymbol{x}})\) is adjusted point-by-point. Notably, this approach eliminates the need to construct an additional probability model to surrogate the constraint function $c(\hat{\boldsymbol{x}}) $. Consequently, Equation \ref{eq:17} can be reformulated as $\alpha_{\text{EI-C}}(\hat{\boldsymbol{x}}) =ND(||c(\hat{\boldsymbol{x}})-c^*||)\alpha_{\text{EI}}(\hat{\boldsymbol{x}})
$.

Figure \ref{fig:6} schematically illustrates the comparison between the constraint-unaware active learning process and the constraint-aware active learning process. The optimal point in the constraint-unaware objective function is denoted by blue dot (Fig \ref{fig:6}a), while the optimal point in the constraint-aware objective function is denoted by red dot (Fig\ref{fig:6}b). We introduced a constraint function expressed by a normalized function to alters the EI score of candidates in a virtual data space, which is evident in the shift of the most promising point to query, as depicted from Fig. \ref{fig:6} c to Fig \ref{fig:6}d (more details about the toy problem are provided in Supplementary S3). The method can accurately found the optimal point in the constraint-aware objective function. Notably, the selection of the subsequent query point, whether driven by prediction (exploitation), uncertainty (exploration), or a trade-off between the two, will be influenced by the constraints.

\section{Results and Discussions}

\subsection{Database of TPMS-based cellular structures }

The Shcoen's gyroid (G) and diamond (D) structures of TPMS present a highly versatile geometry with notably wide range of elastic modulus \citep{Lee2016}. The structures of G and D are defined through the following implicit functions $f(x,y,z)$:
\begin{equation}
\begin{aligned}
f_G(x,y,z)&= cos(2\pi y)sin(2\pi x)+cos(2\pi x)sin(2\pi z)\\&+cos(2\pi z)sin(2\pi y)+t_1 = 0, t_1 =0
\end{aligned}
\label{eq:15}
\end{equation}
\begin{equation}
\begin{aligned}
f_D(x,y,z)&=cos(2\pi x)cos(2\pi y)cos(2\pi z)\\&-sin(2\pi x)sin(2\pi y)sin(2\pi z)+t_2=0, t_2 =0
\end{aligned}
\label{eq:16}
\end{equation}
In addition to concise representation, TPMS-based cellular unit also can be diversified by combining several functions and adjusting corresponding coefficients \citep{Wang2019b}. In the work, the cellular structures are created as a combination of G and D structures, and the weight sum of their implicit functions are denoted by:
\begin{equation}
\begin{aligned}
    f_{Hybrid}(x, y, z) &=\alpha_1 (4f_G(x,y,z))+\alpha_2(4f_D(x, y,z ))\\
    \alpha_1+\alpha_2 &= 1,
    0\leq\alpha_1, \alpha_2 \leq1,
\end{aligned}
\label{eq:17}
\end{equation}
where $\alpha_1$ and $\alpha_2$ are randomized with a fixed sum of 1 to generated diverse cellular structures. The level set value $t_1$ and $t_2$ are limited in range from -0.5 to 0.5, which determine the volume fraction (i.e., relative density ) of a unit cell by thickening or thinning the surfaces. By varying the parameters $\alpha_1, \alpha_2, t_1, t_2$ in Eq.\ref{eq:4}, the TPMS structures can be adjusted, as illustrated in Fig\ref{fig:2}a. The merging operation not only produces geometric variations but also influences the mechanical properties of TPMS unit cells.

We construct a rich database of TMPS unit cell by perturbing the parameters $\{\alpha_1, \alpha_2, t_1, t_2\} $ through Latin hyper-cube sampling (LHS) , resulting in 1372 unique structures (exclude some invalid structures). These structures exhibit orthotropic isotropic mechanical properties due to the cubic symmetric property of merged TPMS unit cell. For each structure, the effective mechanical stiffness tensor was computed by numerical homogenization method as illustrated in Section \ref{subsec:homo}. The mechanical properties of the cellular materials are influenced by both the scaffold architecture and the constituent materials. In the work, Ti6Al4V (Ti) was used as the constituent materials for orthopedic implants \citep{Peng2023} (material's parameters are provided in Supplementary S1). Ti alloy is bio-inert in human bodies and has been the de facto choice for 3D-printed orthopedic implants, achieving successful clinical applications in repairing bone defects. Figure \ref{fig:2}b shows the mechanical properties' distribution (effective elastic modulus $E$, Possion's ratio $v$) of G, D and Hybird TPMS unit cells (The mechanical properties of G and D were computed for an additional 100 samples, which are not included in the dataset of 1372 samples). The distributions of Possion's ratio of G and D exhibit single curve-like distributions with relative density and the Possion's ratio generally decrease as relative density increase, while hybrid TPMS unit cells exhibit significant broader property distribution. The relationship between effective elastic modulus $E$ and relative density $\rho$ follows an exponential form $E \propto E_s\rho^{n}$ (more details are provided in Supplementary S1), as founded in previous research \citep{Bauer2017}.

\begin{figure}
    \centering
    \includegraphics[width=0.75\linewidth]{figures/2.pdf}
    \caption{\textbf{Overview of the} \textbf{structure variation and} \textbf{property} \textbf{distribution} \textbf{of merged TPMS unit cells}. \textbf{a} Examples of different merged TPMS unit cell’s structure are realized by varying the shape parameters $\alpha_1, \alpha_2,t_1,t_2$ of Gyroid (G) and Diamond (D).\textbf{ b }The Effective elastic modulus $E$, Possion’s ratio $v$ and relative density $\rho$ in dataset (plasma colormap). The size of markers is proportional to $E$. Property variation of G and D structures with the increasing $t_i( i=1,2,\Delta t = 0.01$) within $f_G$ and $f_D$, each with a size of 100 are evaluated separately for comparison (bone and viridis colormap, respectively).}
    \label{fig:2}
\end{figure}

\subsection{Performance of TPMS-WGAN}

To train a TPMS-GAN for generating a virtual design space with a target elastic modulus, we enable the elastic modulus condition while disabling other conditions in condition module. The database of hybrid TPMS unit cells is split with a ratio of 8:2 for training (1098) and testing (274), respectively. The coefficients $\alpha_1, \alpha_2$ of implicit function in database and the condition of elastic modulus $E$ are normalized before input to TPMS-GAN (more details are provided in Supplementary S4). We further improve the generative performance by ensuring the generated shape parameters can be accurately mapped back to their corresponding properties. Specially, we add a property navigator $R_\omega$ to predict the elastic modulus of each design. This lead to a additional loss terms:
\begin{equation}
\mathcal{L}_{(R_\omega)}=\mathbb{E}_{\boldsymbol{p}' \sim \mathbb{P}_g}(|R_\omega(\boldsymbol{p}')-E|)
\label{eq:18}
\end{equation}
Combining Eq. \ref{eq:7}, the final discriminator loss can be written by:
\begin{equation}
\mathcal{L}_{D_\theta} =  \mathcal{L}_{(G_\phi, D_\theta)} + \eta *\mathcal{L}_{R_\omega}
\label{eq:19}
\end{equation}
where $\eta$ is a hyperparameter set to 0.5, and the generator loss can be written by 
\begin{equation}
\mathcal{L}_{G_\phi} =  - \mathbb{E}_{\boldsymbol{z}\sim \mathcal{N}(\boldsymbol{0},\boldsymbol{I})} \left[ D_\theta (G_\phi(\boldsymbol{z}|\boldsymbol{C})\right]
\label{eq:20}
\end{equation}
Figure \ref{fig:4} provides a schematic comparison between the navigator-free TPMS-WGAN and the navigator TPMS-WGAN  (the hyper-parameters and architecture are provided in Supplementary Table S2). As depicted in Figure \ref{fig:4}a, the training loss of the navigator-generator, represented by the blue line, is more stable than that of the navigator-free generator, indicated by the green line. In WGAN, the discriminator's loss value serves as an indicator of model performance. Notably, the navigator discriminator exhibits a lower loss value of 2.57, compared to the navigator-free discriminator, which has a loss value of 3.12. Next, we use t-SNE and kernel smoothing function estimate (KSFE) based on the structure parameters of TPMS unit cell for the 2D visualization of the test data. As illustrated in Fig \ref{fig:4}c, d, the data distribution generated by the navigator generator more closely resembles the distribution of the training data compared to that produced by the navigator-free generator. To further assess the quality of the data generated by the navigator generator, we computed the Wasserstein distances \citep{Villani2008OptimalTO}. The results indicate a Wasserstein distance of \textbf{0.23} between the test data and the data generated by the navigator-free generator, and a distance of \textbf{0.34} between the test data and the data generated by the navigator generator. The diagonal plots of elastic modulus of test data and that evaluated of generated data of navigator-free generator and navigator generator via random forest model are shown in Fig \ref{fig:4}e, f (more details about random forest model as a surrogate model are provided in Supplementary S5). The elastic modulus of the structure generated by the navigator generator aligns more closely with the test data's elastic modulus than that produced by the navigator-free generator, with coefficients of determination ($R^2$) of 0.982 and 0.706, respectively. These results indicate that the navigator module effectively guides the gradient descent orientation of TPMS-GAN during training, enhancing its generative performance.

\begin{figure}
    \centering
    \includegraphics[width=0.75\linewidth]{figures/4.pdf}
    \caption{\textbf{Evaluation} \textbf{of} \textbf{the} \textbf{TPMS-GAN} \textbf{model. a} The loss value of navigator-free generator (green line) and navigator generator (blue line) during the training process. \textbf{b} The loss value of navigator-free discriminator (orange line) and navigator discriminator (red line) during the training process. The 2D t-SEN plot of training data distribution (viridis colormap) and generated data distribution (plasma colormap) under the corresponding elastic modules for navigator-free generator (\textbf{c}) and navigator generator (\textbf{d}), respectively. The density represents the probability estimate per unit area. The conditional elastic modulus and the evaluated elastic modulus of the generated structure of navigator-free generator (\textbf{e}) and navigator generator (\textbf{f})}.
    \label{fig:4}
\end{figure}

The continuous and low-dimensional latent space with generative cabilities is particularly advantageous for designing new structures by navigating this space through simple arithmetic operations on the latent representation $\boldsymbol{z}$. However, A general conditional WGAN lacks the ability to map a real structure to its latent space. To address the limitation, we trained an encoder, denoted as $IG_\psi$ to approximate inverse this mapping $(\boldsymbol{z},\boldsymbol{C})=IG_\psi(\boldsymbol{p})$. This inversion enables us to obtain a latent representation $\boldsymbol{z}$ from a real TPMS structure $\boldsymbol{p}$, facilitating exploration of the latent space through interpolation or variation. Although existing parameter-based and pixel/voxel-based generative models for cellular materials have successfully mapped topology and mechanical properties to a latent space using a similar data-driven design framework, they struggle to provide explainability in manipulating the geometry of TPMS unit cells via latent space or implicit function coefficients. By integrating a TPMS-GAN, once the latent representation $\boldsymbol{z}$ is obtained, explicit geometric control can be applied to a structure through geometric conditions. We term this framework Inversed TPMS-GAN (ITPMS-GAN). In this approach, the parameters $\boldsymbol{p}$ of the TPMS structure are encoded into a latent space $\boldsymbol{z}'$, together with the edited geometry condition $\bar{\boldsymbol{s}}$, serve as input into a well-trained generator. The generator then produces the parameters $\boldsymbol{p}'$ of the TPMS structure. Our methodology involves training the inverse mapping encoder $IG_\psi$ after the TPMS-GAN has been trained. To train $IG_\psi$, we utilize the structure parameters $\boldsymbol{p}$ of the TPMS unit cell and the generated parameters $\boldsymbol{p}'$ from the TPMS-GAN, minimizing a squared reconstruction loss $\mathcal{L}_{IG}$ (Fig \ref{fig:5}a).
\begin{equation}
    \mathcal{L}_{IG} = \frac{1}{m}\sum_{i=1}^m(\boldsymbol{p}^{(i)}-\boldsymbol{p}'^{(i)})= \frac{1}{m}\sum_{i=1}^m(\boldsymbol{p}^{(i)}-IG_\psi(\boldsymbol{z}',\bar{\boldsymbol{s}})^{(i)})
\label{eq:21}
\end{equation}
where $m$ is batch size, and the detail hyperparamenters and architecture of ITPMS-GAN are provided in Supplementary Table S4. A major advantage of ITPMS-GAN is its flexibility, allowing for explainable structural editing. As illustrated in Figure \ref{fig:5}b, the pore diameter of a TPMS unit cell from the test set can be edited using ITPMS-GAN. A TPMS unit cell, characterized by a relative density of\textbf{ 0.32 mm}, a pore diameter of \textbf{21 mm}, and a thickness of \textbf{14 mm}, is represented by a geometry vector $\boldsymbol{s}$ (Fig \ref{fig:5}b (iii)). To adjust the pore diameter in $\boldsymbol{s}$ to 19 mm, 20 mm, 21 mm, 22 mm, and 23 mm, we first map the structure parameters $\boldsymbol{p}$ to the latent representation $\boldsymbol{z}'$. This latent representation, combined with the specified pore diameter as a condition, serves as input to $G_\phi^2$ (more details about $G^2_\phi$ are provided in Supplementary Table S3). The generated TPMS structures exhibit a gradual variation corresponding to the variations of pore diameter, as depicted in Fig \ref{fig:5}b. We conducted simulations to assess the geometric characteristics of the generated structures. The actual geometries closely matched the designed ones, except for pore diameters of 19 mm and 23 mm, which measured 18.5 mm and 24 mm, respectively. In the 2D t-SNE plot of the training dataset structures (Fig \ref{fig:5}c), the generated structures are visualized to assess their spatial distribution. The structure with a pore diameter of 19 mm is located on the boundary of the TPMS structure, with the design error primarily resulting from the limited data available in the training set, hindering the model's ability to learn its features. Furthermore, there is a significant discrepancy between the pre-set and validated pore diameters for 23 mm and 24 mm. Figure \ref{fig:5}c also reveals that the structure \textbf{v} is positioned far from other designed structures, forming a distinct D-like shape, and exhibits greater similarity to structure G. The ITPMS-GAN model offers an explainable method for editing TPMS unit cells, instead of interpolation in latent space or adjusting implicit function coefficients. The approach can be applied to diverse structures in virtual design space or create a more refined design space.

\begin{figure}
    \centering
    \includegraphics[width=1\linewidth]{figures/5.pdf}
    \caption{\textbf{Inversed TPMS-GAN (ITPMS-GAN) and representative examples of editing geometry of TPMS unit cells. a} The implicit function parameters $\boldsymbol{p}$ of TPMS unit cell with geometry features $\boldsymbol{s}$ is encode to latent vector $\boldsymbol{z}'$ by ITPMS-GAN, $IG_\psi$. And then the latent representation $\boldsymbol{z}'$ and the edited structure parameters $\bar{\boldsymbol{s}}$ are passed to generator $G_\phi^2$ to construct the TPMS unit cell. \textbf{b} The corresponding geometry evolution of TPMS unit cell is shown along the size variation of pore diameter. The designed pore diameters of TPMS unit cells by ITPMS-GAN are depicted as red dots, while the measured pore diameters are represented by blue dots. \textbf{c} The 2D t-SEN plot of implicit function parameters of training data (blue dots) and five designed TPMS unit cell (red stars). The structure evolution path of these five designed TPMS unit cells in the reduced parameters space of implicit function is shown by a black dashed line. }
    \label{fig:5}
\end{figure}

Bone is a typical cellular material primarily consisting of cortical and cancellous parts, with the elastic modulus ($E$) ranging from 30 to 30,000 MPa depending on the bone mineral density and varying according to age, sex, and race \citep{Wang2016}. Although bone can repair itself, a bone defect of a critical size necessitates a grafting implant to support the load and induce bone growth. For the application of TPMS unit cell in bio-implants, the two targets need to be optimized: (1) the $E$ of the scaffold implant must match that of the bone to relief stress shielding effect and frost the recovery of the bone \citep{Yang2020}. (2) the $\sigma_{ys}$ must be as high as possible to sustain the bone.

In  the work, we employed the TPMS-GAN $G_\phi^1$ to generate 100,000 TPMS structures, forming a virtual design space $\Omega_E$ with a target elastic modulus of 6,000 MPa. As depicted in Figure \ref{fig:6}e, we compared the elastic modulus of these generated structures, as evaluated by a random forest model, with the pre-set value of 6,000 MPa (denoted by a red dashed line). The observed elastic modulus values ranged from 5,400 MPa to 6,300 MPa, clustering around the target modulus. To incorporate this target into constraint-aware active learning, we defined a constraint function based on the deviation of the generated structures' elastic modulus from the pre-set value of 6,000 MPa. This function is expressed as:
\begin{equation}
    c(\boldsymbol{p}') = 1 - \frac{|E(\boldsymbol{p}') - 6000|}{\max(|E(\boldsymbol{p}') - 6000|)}
\label{eq:22}
\end{equation}
The function $c(\boldsymbol{p}')$ reaches its maximum value when $E(\boldsymbol{p}') = 6000$. Figure \ref{fig:6}f illustrates the application of this constraint function within the virtual design space.

\begin{figure}
    \centering
    \includegraphics[width=0.75\linewidth]{figures/6.pdf}
    \caption{\textbf{Schematical figure of constrained-aware active learning strategy. a} The optimal value and predicted results with uncertainties in the cases of constraint-unaware (\textbf{a1}) and constraint-aware (\textbf{a2}). \textbf{b} The next query point according to EI (\textbf{b1}) and constrained-aware EI (\textbf{b2}). \textbf{c} The virtual design space of TPMS unit cell with a target elastic modulus of 6,000 MPa generate by generator $G_\phi^1$. \textbf{d} The application of elastic modulus constraint function within the virtual design space.}
    \label{fig:6}
\end{figure}

\subsection{Develop high yield strength TPMS unit cells with matched elastic modulus via the constraint-Aware Strategy}

The properties of the cellular materials are determined by both the scaffold architecture and the constituent materials. The mechanical response of the scaffold can be represented by a compressive stress-strain curve. Yield strength ($\sigma_{ys}$) is denoted by the yield point with 0.2 \% strain, which quantifies the maximum resistance prior to the onset of irreversible deformation. Calculating $\sigma_{ys}$ through simulation is resource-intensive due to the nonlinear plastic behavior of the constituent materials and the extensive number of discrete meshes involved. The yield strength calculation for each TPMS unit cell takes approximately 30 minutes, which is longer than the elastic modulus evaluation time of about 1 minute using FE simulation based on the numerical homogenization method (Details about computing platform are provided in Supplementary S6). BO method is efficiently to applied into expensive-to-evaluate black box problem. Here we propose an active learning approach to optimize yield strength while adhering to constraints on the elastic modulus. A support vector machine model is employed as the surrogate model, and bootstrap resampling is utilized to assess uncertainties by sampling the data with replacement. In present study, we sampled 16 candidates from the virtual design space and evaluated their yield strength using FEM. This process was repeated 50 times, generating 50 resampled training sets to construct 50 support vector machine models. Consequently, each sample in the initial dataset yields 50 predicted values, which are used to determine the mean value ($\mu$) and the associated standard deviation ($\Sigma$).

Figure \ref{fig:7}c illustrates the transition of the query sample from the blue dot to the red dot at the 1st iteration, facilitated by the elastic modulus constraint-aware EI approach introduced in \ref{sec:2-4}. This shift indicates that the constraint function of the elastic modulus alters the maximum expected improvement over the best observed value in the training dataset. A total of four iterations are performed, during which two samples are recommended and evaluated per iteration. The results are subsequently fed back into the dataset to initiate a new iteration.

The diagonal plot in Fig \ref{fig:7}a reveals that the model predictions are basically consistent with the observation values and the strategy of constraint-aware active learning recommended samples with high yield strength. We monitor mean square error (MSE) and R$^2$ as the surrogate model is successively refined with the results of evaluated TPMS structures  (Fig. \ref{fig:7}b).

The elastic modulus and yield strength of all recommended samples are presented in Fig \ref{fig:7}(d,e,f). It is observed that the elastic modulus of these samples is closer to 6,000 MPa, with a mass center around 5,900 MPa, compared to the initial dataset, which has a mass center of approximately 5,800 MPa. Additionally, the yield strength of the recommended samples surpasses that of the initial dataset. To further demonstrate the efficacy of the constraint-aware active learning framework, the overall performance $Y$ of the TPMS unit cell is quantified by the following equation:

\begin{equation}
    Y = Y_E^N+Y_{\sigma_{ys}}^N
\label{eq:23}
\end{equation}
where 
\begin{equation}
    \begin{aligned}
    Y_E^N &= \frac{Y_E-\text{min}(Y_E)}{\text{max}(Y_E)-\text{min}(Y_E)} 
 ,Y_E = \frac{1}{|E(\boldsymbol{p}')-E^*|}\\
    Y^N_{\sigma_{ys}}& =\frac{Y_{\sigma_{ys}}-\text{min}(Y_{\sigma_{ys}})}{\text{max}(Y_{\sigma_{ys}})-\text{min}(Y_{\sigma_{ys}})} 
    \end{aligned}
\label{eq:24}
\end{equation}

This metric effectively reflects the design performance of TPMS unit cell in achieving a matched implant scaffold with enhanced yield strength.

Figure \ref{fig:7}g indicates that the optimal structure was identified at the 2nd iteration, with a $Y$ value of 1.72, significantly higher than the optimal value of 0.22 in initial dataset. At the 3rd iteration, a decrease in overall performance was observed due to the active learning process, which integrates both exploration and exploitation capabilities. However, this approach led to improved performance at the 4th iteration. The stress-strain curve is depicted in Figure \ref{fig:7}i, while Figure \ref{fig:7}h presents the Von Mises' stress cloud plot. It is evident that stress concentration is localized at the junctions of unit cells. This study demonstrates that the constraint-aware active learning method successfully identified the optimal structure even beyond the training dataset, indicating a degree of extrapolation capability. Such robustness is particularly advantageous in clinical scenarios, where patient data, including target material properties and mechanical ranges, are often unknown in advance, and initial data distributions can vary widely. Furthermore, the design cost of TPMS unit cells with matched elastic modulus and high yield strength is significantly reduced by employing a method that requires the assessment of only 24 sample yield strengths. This is in stark contrast to the 1372 assessments needed in the one-step machine learning method used for training the generative model under bi-objective conditions. As a result, the design time is reduced about sixfold.

\begin{figure}
    \centering
    \includegraphics[width=1\linewidth]{figures/7.pdf}
    \caption{\textbf{Active learning workflow for yield stress of TPMS unit cells with elastic modulus constraint. a} Diagonal plot for SVM showing in red are the recommended structures and the green represents the initial data. \textbf{b} Performance of the SVM regressor as the iterations proceed. \textbf{c} Comparison of query points between EI and elastic modulus constraint-aware EI at 1st iteration. \textbf{d} Elastic modulus of the recommended structures as the iterations proceed. \textbf{e} The elastic modulus and yield strength distribution of recommended structures and the initial data (blue dots). \textbf{f} The elastic modulus and yield strength of recommended structures at each iteration of active learning. \textbf{g} The overall performance of TPMS unit cells as the iterations proceed. \textbf{h} The simulation strain-stress curves of the optimal structure recommended and the optimal 
structure in initial data. \textbf{g} The Von Mises' stress cloud plot of the optimal structure recommended in active learning.}
    \label{fig:7}
\end{figure}

\section{Conclusions}

In summary, a data-efficient two-stage bi-objective inverse design method of cellular materials based on TPMS is proposed, which combines generative model, active learning and FEM. The approach considers the unbalanced costs associated with different objectives. The cubic symmetric TPMS unit cells (G and D) were megred to create the rich dataset of isotropic cellular material in which the effective elastic tensor are calculated using a voxel-based numerical homogenization method. Our proposed TPMG-GAN with a navigator can generate the TPMS unit cells under desired conditions, here we generate TPMS unit cells under a target elastic modulus. The inversed TPMS-GAN also developed to

% We proposed a GAN model to learn the IH mapping from properties to unit cell shapes that can be used to optimize functionally graded cellular structures. The cubic symmetric TPMS surfaces (P, D, and F-RD) were chosen and combined to create the dataset of isotropic cellular structures and represent each cellular unit cell as a six-dimensional shape vector (i.e., α1, α2, α3, t1, t2, t3). The unit cell property space consists of effective Young’s modulus, Poisson’s ratio, and relative density (i.e., E H , ν H , and ρ) in which E H and ν H were computed using a voxel-based numerical homogenization method. Our proposed IH-GAN’s one-to-many IH mapping was learned on the six-dimensional shape parameter space with the three-dimensional property space as the input conditions. Our approach offers an end-to-end generative model that automatically learns the IH mapping from data without assuming a bijective polynomial relationship. Except for the unit cell density (volume fraction), we also consider unit cell types when building the mapping. By including an auxiliary regressor in the IH-GAN, we can accurately generate the cellular unit cells that possess the desired properties (R2-scores between target properties and properties of generated unit cells > 98%). We also demonstrate the IH-GAN model’s efficacy by implementing it on modified structural optimization problems to construct multi-scale functionally graded cellular structures (e.g., a cantilever beam in this paper) using multiple types of cellular unit cells. Our approach addresses the connectivity issue between different types of unit cells simultaneously without a need for further compatibility optimization. By performing FE simulations, we validate that the beam constructed by IH-GAN improves the functional performance (e.g., 79.7% reduction in concentrated stress) compared to the conventional variable-density single-type beam structure. Moreover, the beam redesigned by IH-GAN can also achieve the target deformations with decent performance.

\section*{CRediT authorship contribution statement}
Jiaxuan Ma: Writing – original draft, Software, Methodology, Investigation, Formal analysis, Conceptualization. Bin Cao: Software, Investigation, Conceptualization, Formal analysis. Yuan Tian: Writing – review \& editing, Investigation, Formal analysis. Sheng Sun: Writing – review \& editing, Supervision, Funding acquisition, Formal analysis.

\section*{Declaration of competing interest}
The authors declare that they have no known competing financial interests or personal relationships that could have appeared
to influence the work reported in this paper.

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% If you have bibdatabase file and want bibtex to generate the
%% bibitems, please use
%%
\bibliographystyle{elsarticle-harv} 
\bibliography{refs}

%% else use the following coding to input the bibitems directly in the
%% TeX file.

% \begin{thebibliography}{00}

% %% \bibitem[Author(year)]{label}
% %% Text of bibliographic item

% \bibitem[ ()]{}

% \end{thebibliography}
\end{document}

\endinput
%%
%% End of file `elsarticle-template-harv.tex'.

### 2025-01-26 manuscript.tex
update on mac 2025-01-27

@@
 \begin{abstract}
-Implicit surface-based cellular materials have gained widespread adoption in bone scaffolds applications due to their similarities to bone structure.
-These materials excel in providing good mechanical properties and bioadaptability, creating suitable conditions for bone tissue regeneration.
-However, the rational design of these materials typically depends on prior knowledge of experts and requires large of  trail-and-error experiments.
-Here, we present a data-efficient two-stage bi-objective optimization method within a machine learning framework that considers the varying costs associated different objectives.
-Specifically, we employ this methodology to orthopedic implant inverse design, integrating generative model, active leaning, and finite element analysis to achieve both biocompatible elastic modulus and higher yield strength cellular materials.
-Our approach demonstrates remarkable improvements in overall performance compared to initial datasets, while simultaneously reducing about sixfold design cost relative to one-step bi-objective optimization machine learning method.
-This methodology establishes an efficient paradigm for the rapid and intelligent design of cellular materials with tailored mechanical properties, particularly valuable in scenarios involving objectives with unbalanced computational costs.
+Implicit surface-based cellular materials have gained significant attention in bone scaffold applications due to their structural resemblance to natural bone.
+These materials exhibit excellent mechanical properties and bioadaptability, providing an ideal environment for bone tissue regeneration.
+However, the rational design of such materials often relies heavily on expert knowledge and extensive trial-and-error experiments.
+In the work, we propose a data-efficient, two-stage bi-objective optimization framework within a machine learning paradigm, which accounts for the disparate computational costs associated with different objectives.
+Specifically, we apply this methodology to the inverse design of orthopedic implants, integrating a generative model, active learning, and finite element analysis to achieve cellular materials with both biocompatible elastic modulus and enhanced yield strength.
+Our approach demonstrates significant improvements in overall performance compared to the initial dataset, while reducing design costs by approximately sixfold relative to conventional one-step bi-objective machine learning optimization methods.
+This framework establishes an efficient paradigm for the rapid and intelligent design of cellular materials with tailored mechanical properties, particularly in scenarios where objectives involve unbalanced computational costs.
 \end{abstract}
@@
 \begin{highlights}
-\item Developing TPMS-GAN with navigator was proposed to generate TMPS unit cell under desired conditions of mechanical properties and geometries.
-\item Developing Inversed TPMS-GAN to design TPMS unit cell in geomety feature in a explainable way instead of through latent space or coefficients of implicit function 
-\item Proposing a constraint-aware active learning method to address bi-objective optimization problem with unbalanced costs of objective function. 
+\item A TPMS-GAN with a navigator was developed to generate TPMS unit cells under desired mechanical and geometric conditions.
+\item An Inverse TPMS-GAN was introduced to design TPMS unit cells directly from geometric features in an explainable way, bypassingneed to interpolate in latent space or modify implicit function coefficients.
+\item A constraint-aware active learning method was proposed to address bi-objective optimization problems with unbalanced objective function costs.
 \end{highlights}
@@
 Consequently, machine learning models can be seamlessly integrated into heuristic algorithms facilitating the optimization of cellular material structures with target mechanical properties, such as elastic modulus \citep{Garland2021,Lee2022,Chen2024b}, bulk resistance \citep{Liu2020a}, and stress-strain curve \citep{Deng2022a,Ma2020b}.
-However, surrogate optimization is a high-throughput selection process that necessitates multiple invocations of machine learning models, presenting challenges for global optimization problems and real-time design requirements.
+However, surrogate optimization is a high-throughput selection process that requires multiple invocations of machine learning models, presenting challenges for global optimization problems and real-time design requirements.
 
@@
 However, this approach led to improved performance at the 4th iteration.
-The stress-strain curve is depicted in Figure \ref{fig:7}i, while Figure \ref{fig:7}h presents the Von Mises' stress cloud plot.
+The stress-strain curve is depicted in Figure \ref{fig:7}i, while Figure \ref{fig:7}h presents the von Mises stress cloud plot.
 It is evident that stress concentration is localized at the junctions of unit cells.
@@
 \textbf{h} The simulation strain-stress curves of the optimal structure recommended and the optimal
-structure in initial data. \textbf{g} The Von Mises' stress cloud plot of the optimal structure recommended in active learning.}
+structure in initial data. \textbf{g} The von Mises' stress cloud plot of the optimal structure recommended in active learning.}
     \label{fig:7}
@@
 
-In summary, a data-efficient two-stage bi-objective inverse design method of cellular materials based on TPMS is proposed, which combines generative model, active learning and FEM.
-The approach considers the unbalanced costs associated with different objectives.
-The cubic symmetric TPMS unit cells (G and D) were megred to create the rich dataset of isotropic cellular material in which the effective elastic tensor are calculated using a voxel-based numerical homogenization method.
-Our proposed TPMG-GAN with a navigator can generate the TPMS unit cells under desired conditions, here we generate TPMS unit cells under a target elastic modulus.
-The inversed TPMS-GAN also developed to
-
-% We proposed a GAN model to learn the IH mapping from properties to unit cell shapes that can be used to optimize functionally graded cellular structures.
-The cubic symmetric TPMS surfaces (P, D, and F-RD) were chosen and combined to create the dataset of isotropic cellular structures and represent each cellular unit cell as a six-dimensional shape vector (i.e., α1, α2, α3, t1, t2, t3).
-The unit cell property space consists of effective Young’s modulus, Poisson’s ratio, and relative density (i.e., E H , ν H , and ρ) in which E H and ν H were computed using a voxel-based numerical homogenization method.
-Our proposed IH-GAN’s one-to-many IH mapping was learned on the six-dimensional shape parameter space with the three-dimensional property space as the input conditions.
-Our approach offers an end-to-end generative model that automatically learns the IH mapping from data without assuming a bijective polynomial relationship.
-Except for the unit cell density (volume fraction), we also consider unit cell types when building the mapping.
-By including an auxiliary regressor in the IH-GAN, we can accurately generate the cellular unit cells that possess the desired properties (R2-scores between target properties and properties of generated unit cells > 98%).
-We also demonstrate the IH-GAN model’s efficacy by implementing it on modified structural optimization problems to construct multi-scale functionally graded cellular structures (e.g., a cantilever beam in this paper) using multiple types of cellular unit cells.
-Our approach addresses the connectivity issue between different types of unit cells simultaneously without a need for further compatibility optimization.
-By performing FE simulations, we validate that the beam constructed by IH-GAN improves the functional performance (e.g., 79.7% reduction in concentrated stress) compared to the conventional variable-density single-type beam structure.
-Moreover, the beam redesigned by IH-GAN can also achieve the target deformations with decent performance.
+In summary, this study proposes a data-efficient, two-stage bi-objective inverse design method for cellular materials based on TPMS.
+The method integrates a generative model, active learning, and finite element analysis, while accounting for the unbalanced costs associated with different objectives.
+Specifically, the methodology is applied to the inverse design of orthopedic implants.
+For TPMS-based bio-implants, two critical objectives are optimized: (1) the elastic modulus ($E$) of the scaffold implant must match that of the bone to mitigate the stress-shielding effect and promote bone recovery , and (2) the yield strength ($\sigma_{ys}$) must be maximized to ensure mechanical stability under load.
+Initially, cubic symmetric TPMS unit cells (G and D) were merged to create a comprehensive dataset of isotropic cellular materials, with the effective elastic tensor calculated using a voxel-based numerical homogenization method.
+The proposed TPMG-GAN, equipped with a navigator, generates TPMS unit cells under specified conditions, enabling the creation of a virtual structure space tailored to a target elastic modulus.
+Furthermore, an ITPMS-GAN was developed to design TPMS unit cell structures directly from geometric features in an explainable way, bypassing the need to interpolate in latent space or modify implicit function coefficients.
+This approach not only diversifies the virtual structure space but also provides a novel pathway for TPMS structure design.
+Finally, a constraint-aware active learning framework was extended to optimize yield strength under elastic modulus constraints, achieving a significant performance improvement from 0.2 to 1.7 compared to the initial dataset.
+This study demonstrates that the constraint-aware active learning method successfully identifies optimal structures even beyond the training dataset, showcasing its extrapolation capability.
+Additionally, the design time is reduced approximately sixfold compared to traditional one-step bi-objective machine learning methods.
 

### 2025-02-01 manuscript.tex
update on mac 2025-01-27
update on mac 2025-0201

@@
 
-\title{Inverse design workflow of implicit surface-based cellular materials via conditional generative model and active Learning}
+\title{Inverse design workflow of implicit surface-based cellular materials via conditional generative model and active learning}
 
@@
 \author[3]{Bin Cao}
-\author[1]{Yuan Tian, \corref{cor1}}
+\author[1]{Yuan Tian\corref{cor1}}
 \ead{tian0321@shu.edu.cn}
-\author[1,2]{Sheng Sun, \corref{cor1}}
+\author[1,2]{Sheng Sun\corref{cor1}}
 \ead{mgissh@t.shu.edu.cn}
@@
 Our approach demonstrates significant improvements in overall performance compared to the initial dataset, while reducing design costs by approximately sixfold relative to conventional one-step bi-objective machine learning optimization methods.
-This framework establishes an efficient paradigm for the rapid and intelligent design of cellular materials with tailored mechanical properties, particularly in scenarios where objectives involve unbalanced computational costs.
+This framework establishes an efficient paradigm for the rapid and intelligent design of cellular materials with tailored mechanical properties, particularly in scenarios where objectives involve imbalanced computational costs.
 \end{abstract}
@@
 \begin{highlights}
-\item A TPMS-GAN with a navigator was developed to generate TPMS unit cells under desired mechanical and geometric conditions.
-\item An Inverse TPMS-GAN was introduced to design TPMS unit cells directly from geometric features in an explainable way, bypassingneed to interpolate in latent space or modify implicit function coefficients.
-\item A constraint-aware active learning method was proposed to address bi-objective optimization problems with unbalanced objective function costs.
+\item A TPMS-GAN with a navigator was developed to generate TPMS unit cells meeting specific mechanical and geometric conditions.
+\item An inversed TPMS-GAN was introduced to design TPMS unit cells directly from geometric features in an explainable way, bypassing the need to interpolate in latent space or adjust implicit function coefficients.
+\item A constraint-aware active learning method was proposed to tackle bi-objective optimization problems with imbalanced objective function costs.
 \end{highlights}
@@
 In this step, a TPMS-GAN model is trained on a dataset containing TPMS unit cells and their corresponding elastic modulus.
-Then the generator of the TPMS-GAN produces structures with target elastic modulus, forming a virtual structure space (VSS).
-(2) inversed TPMS-GAN (ITPMS-GAN) model was developed to explore the latent space of TPMS-GAN, allowing for direct geometric manipulation of TPMS structures instead of modifying implicit function parameters.
+Then the generator of the TPMS-GAN produces structures with target elastic modulus, forming a virtual design space ($\Omega_E$).
+(2) inversed TPMS-GAN (ITPMS-GAN) model was developed to explore the latent space of TPMS-GAN, allowing for direct geometric manipulation of TPMS structures instead of adjusting implicit function parameters.
 (3) an elastic modulus constraint-aware active learning approach for yield strength optimization.
-Initially, the yield strength of a select number of TPMS structures within VSS are evaluated to establish the initial dataset via FEM.
+Initially, the yield strength of TPMS structures selected from $\Omega_E$ are evaluated to establish the initial dataset via FEM.
 Subsequently, elastic modulus constraint-aware active learning based on Bayesian optimization (BO) is employed to optimize the yield strength of TPMS unit cells.
-BO method has been proven significant efficiency in materials design with small data \citep{Ma2024b,Cao2024a,Tian2024a}.
+BO method has been proven significant efficiency in materials design with limited data \citep{Ma2024b,Cao2024a,Tian2024a}.
 
@@
 \textbf{b} The ITPMS-GAN model was developed to edit the TPMS structure through geometry features to rich diversity of candidates in $\Omega_E$.
-\textbf{c} The machine learning (ML) algorithm interactively queries the FEM to discovery new TPMS designs with high yield strength and target elastic modulus through constrained active learning in $\Omega_E$.}
+\textbf{c} The machine learning algorithm interactively queries the FE simulation to discover new TPMS designs with high yield strength and target elastic modulus through constrained active learning in $\Omega_E$.}
     \label{fig:1}
@@
 In this equation, $\hat{\varepsilon}$ is the virtual strain, $\mathbb{C}$ is the elastic tensor of the constituent materials, and $\Omega$ represents the unit cell.
-This equation is numerically discretized and evaluated using the FEM, which employs eight-node hexahedrons to voxelize each unit cell into $40 \times 40 \times 40$ cubes (more details are provided in Supplement S1).
+This equation is numerically discretized and evaluated using the FEM, which employs eight-node hexahedrons to voxelize each unit cell into $40 \times 40 \times 40$ cubes (see Fig S1).
 Once $\varepsilon^{*}$ is obtained, the effective elastic tensor $\mathbb{C}^H$ can be determined using the following equation:
@@
 In this matrix, $E_i$ represents the elastic modulus along the $i^{\text{th}}$ direction, where $i \in \{x, y, z\}$.
-In the work, for cubic symmetric unit cells, we have effective elastic module $E^H=E_x=E_y=E_z$.
-Additionally, elastic moduli in other directions can be obtained from $\mathbb{S}^H$ using the following equation:
+In the work, for cubic symmetric unit cells, we have effective elastic modulus $E^H=E_x=E_y=E_z$.
+Additionally, elastic modulus in other directions can be obtained from $\mathbb{S}^H$ using the following equation:
 \begin{equation}
@@
 \end{equation}
-Here, $E_{ijk}$ is the elastic moduli along the $[i,j,k]$ direction, and $\ell$ is the cosine of the angle between the orientation $[i,j,k]$ and the coordinate axes $[x, y, z]$.
-This approach allows for the evaluation of elastic modulus in any orientation of the unit cell, facilitating the construction of a three-dimensional elastic modulus surface.
+Here, $E_{ijk}$ is the elastic modulus along the $[i,j,k]$ direction, and $\ell$ is the cosine of the angle between the orientation $[i,j,k]$ and the coordinate axes $[x, y, z]$.
+This approach allows for the evaluation of elastic modulus in any orientation of the unit cell, facilitating the construction of a three-dimensional elastic modulus surface (see Fig S1).
 
@@
 
-In the work, we employ a conditional Wasserstein GAN comprising four components: a generator network ($G_\phi$), a discriminator network ($D_\theta$),  a navigator network ($R_\omega$) and a condition module $\boldsymbol{C}$ that consists of mechanical properties and geometry characterization of the TPMS unit cell.
-Each condition can be turned on/off during the training process to meet various design requirements (see Fig.\ref{fig:3} ).
+In the work, we employ a conditional Wasserstein GAN comprising four components: a generator network ($G_\phi$), a discriminator network ($D_\theta$),  a navigator network ($R_\omega$) and a condition module $\boldsymbol{C}$ that consists of mechanical properties and geometric features of the TPMS unit cell.
+Each condition can be turned on/off during the training process to meet various design requirements (see Fig.
+\ref{fig:2}).
 The generator $G_\phi$ (with set of trainable parameters $\phi$) map the Gaussian noise ($z$) and conditions to TPMS's parameter space $\boldsymbol{p}$ in $\mathbb{R}^4$, and achieve the fake $\boldsymbol{p}'$.
@@
 where $D$ belongs to the set of 1-Lipschitz functions, $\mathbb{P}_r$ and $\mathbb{P}_g$ are distribution of dataset and model distribution implicitly defined by $\boldsymbol{p}'=G_\phi(\boldsymbol{z}|\boldsymbol{C}) $, respectively.
-In addition, we employ the Wasserstein GAN gradient penalty (WGAN-GP) method to address the delicate and unstable training issues associated with vanishing or exploding gradients.
-Further details can be found in \citep{Gulrajani2017}.
+In addition, we employ the Wasserstein GAN gradient penalty (WGAN-GP) method to address the delicate and unstable training issues associated with vanishing or exploding gradients \citep{Gulrajani2017}.
 
@@
     \caption{\textbf{Generative modeling framework}.
-The conditional WGAN model can address multiple conditions including property and geometry characterizations of TPMS unit cell, here we called it TPMS-WGAN.
+The conditional WGAN model can address multiple conditions including mechanical and geometric features of TPMS unit cell, here we called it TPMS-WGAN.
 Each condition can be turned on$/$off to meet various design requirements.
-Considering elastic modulus, the TPMS-WGAN takes effective elastic modulus $E$ and random noise $\boldsymbol{z} (\boldsymbol{z}\sim\mathcal{N}(\mathbf{0},\mathbf{I})$,a Gaussian distribution of zero mean and the identity as the covariance matrix) as input to generator $G_\phi^1$, and the generated TPMS structure (denoted by implicit function parameters $\boldsymbol{p}'$), $E$ and the real TPMS structure (denoted by $\boldsymbol{p}$) are then passed to the discriminator $D_\theta$ to output value $f_D$.
+Considering elastic modulus, the TPMS-WGAN takes effective elastic modulus $E$ and random noise $\boldsymbol{z} (\boldsymbol{z}\sim\mathcal{N}(\mathbf{0},\mathbf{I})$, a Gaussian distribution of zero mean and the identity as the covariance matrix) as input to generator $G_\phi^1$, and the generated TPMS structure (denoted by implicit function parameters $\boldsymbol{p}'$), $E$ and the real TPMS structure (denoted by $\boldsymbol{p}$) are then passed to the discriminator $D_\theta$ to output value $f_D$.
 The $\boldsymbol{p}'$ also is passed navigator $R_\omega$ to obtained the predicted effective elastic modulus $E'$.}
-    \label{fig:3}
+    \label{fig:2}
 \end{figure}
@@
 Surrogate model make it possible to search the virtual design space at low computational costs with uncertainty, while AF is employed to evaluate the score of samples in a given virtual design space, considering exploration and exploitation.
-In the work, support vector machine (SVM) model is used to surrogates the expensive objective i.e., the FE calculation of yield stress of the TPMS unit cell.
-Then bootstrap method is utilized to introduce the prediction uncertainties to build the probability model $y=f(\boldsymbol{x})+\varepsilon$.
-The probability model is directly applied to estimate the mean value ($\mu$) and associated uncertainties ($\Sigma^2$) of candidates in a unexplored virtual design space.
+In the work, support vector machine (SVM) model is used to surrogates the expensive objective i.e., the FE calculation of yield strength of the TPMS unit cell.
+Then bootstrap method is utilized to introduce the prediction uncertainties to build the probability model $y=f(\boldsymbol{x})+\varepsilon,\varepsilon\sim(0, \Sigma^2)$.
+The probability model is directly applied to estimate the mean value $f(\boldsymbol{x})$ and associated uncertainty $\Sigma^2$ of candidates in an unexplored virtual design space.
 
 BO is a sequential optimization process that explore the optimal solution through iteration.
-At each iteration, the SVM model is used to evaluate all the unobserved sample within virtual design space, and select the most promising candidate $\hat{\boldsymbol{x}}^*$ for simulation or experiment to obtain $f(\hat{\boldsymbol{x}}^*)$ according to AF.
+At each iteration, the SVM model is used to evaluate all the unobserved samples within $\Omega_E$, and select the most promising candidate $\hat{\boldsymbol{x}}^*$ for simulation or experiment to obtain $f(\hat{\boldsymbol{x}}^*)$ according to AF.
 The obtained new data pair $(\hat{\boldsymbol{x}}^*, f(\hat{\boldsymbol{x}}^*))$ is added to the known data set $\mathcal{D} = \{(\boldsymbol{x}_1, f(\boldsymbol{x}_1)), \ldots, (\boldsymbol{x}_n, f(\boldsymbol{x}_n))\}$ and update SVM to enhance its prediction ability.
@@
 \end{equation}
-A popular utility function is expected improvement (EI) which rewards the large improvement over the best observed value $f^*$ in $\mathcal{D}$ (evaluated thus far), that is:
+A popular utility function is expected improvement (EI) which rewards the improvement over the best observed value $f^*$ in $\mathcal{D}$ (evaluated thus far), that is:
 \begin{equation}
@@
 \end{equation}
-The corresponding AF can now by obtained by substituting Eq. \ref{eq:9} in Eq. \ref{eq:8} and using the reparametrization trick (more details are provided in Supplementaty S2):
+The corresponding AF can now by obtained by substituting Eq. \ref{eq:9} in Eq. \ref{eq:8} and using the reparametrization trick (more details are provided in Supplementaty Note S2):
 \begin{equation}
@@
 where $c(\boldsymbol{x})$ are the other results of data set $\mathcal{D}$, and it is modeled by another probability model similar to $f(\cdot)$.
-The $c(\boldsymbol{x})\leq \lambda$ is a constraint function that limited the feasible area in virtual design space.
+The $c(\boldsymbol{x})\leq \lambda$ is a constraint function that limited the feasible area in a virtual design space.
 The constraint-aware EI for a candidate $\hat{\boldsymbol{x}}$ can be written by:
@@
 where $\Delta_\text{C}(\hat{\boldsymbol{x}})\in \{0,1\}$ is a feasibility indicator function that is 1 if $c(\hat{\boldsymbol{x}})\leq \lambda$, and 0 otherwise. 
-The distribution of random variable $\Delta(\hat{\boldsymbol{x}})$ is Bernoulli distribution:
+The distribution of random variable $\Delta_\text{C}(\hat{\boldsymbol{x}})$ is Bernoulli distribution:
 \begin{equation}
@@
 Thus $\alpha_{\text{EI-C}}(\hat{\boldsymbol{x}})$ is the a standard EI of $\hat{\boldsymbol{x}}$ over the feasible point weighted by the probability that $\hat{\boldsymbol{x}}$ is feasible.
-In the work, we extend the constraint-aware expected improvement AF by surrogate $PF(\hat{\boldsymbol{x}})$ with the normalized distance between the constraint value $c(\hat{\boldsymbol{x}})$ within a virtual space and a target point $c^*$.
+In the work, we extend the constraint-aware expected improvement AF by surrogate $PF(\hat{\boldsymbol{x}})$ with the normalized distance between the constraint value $c(\hat{\boldsymbol{x}})$ and a target point $c^*$.
 This distance is mathematically expressed as $ND(||c(\hat{\boldsymbol{x}})-c^*||)$.
-By incorporating the constrained function, the distribution of \(\alpha_{\text{EI}}(\hat{\boldsymbol{x}})\) is adjusted point-by-point.
+By incorporating the constraint function, the distribution of \(\alpha_{\text{EI}}(\hat{\boldsymbol{x}})\) is adjusted point-by-point.
 Notably, this approach eliminates the need to construct an additional probability model to surrogate the constraint function $c(\hat{\boldsymbol{x}}) $.
-Consequently, Equation \ref{eq:17} can be reformulated as $\alpha_{\text{EI-C}}(\hat{\boldsymbol{x}}) =ND(||c(\hat{\boldsymbol{x}})-c^*||)\alpha_{\text{EI}}(\hat{\boldsymbol{x}})
+Consequently, Equation.
+\ref{eq:17} can be reformulated as $\alpha_{\text{EI-C}}(\hat{\boldsymbol{x}}) =ND(||c(\hat{\boldsymbol{x}})-c^*||)\alpha_{\text{EI}}(\hat{\boldsymbol{x}})
 $.
@@
 Figure \ref{fig:6} schematically illustrates the comparison between the constraint-unaware active learning process and the constraint-aware active learning process.
-The optimal point in the constraint-unaware objective function is denoted by blue dot (Fig \ref{fig:6}a), while the optimal point in the constraint-aware objective function is denoted by red dot (Fig\ref{fig:6}b).
+The optimal point in the constraint-unaware objective function is denoted by blue dot (Fig.
+\ref{fig:6}\textbf{a}), while the optimal point in the constraint-aware objective function is denoted by red dot (Fig.
+\ref{fig:6}\textbf{b}).
 We introduced a constraint function expressed by a normalized function to alters the EI score of candidates in a virtual data space, which is evident in the shift of the most promising point to query, as depicted from Fig.
-\ref{fig:6} c to Fig \ref{fig:6}d (more details about the toy problem are provided in Supplementary S3).
+\ref{fig:6}\textbf{c} to Fig.
+\ref{fig:6}\textbf{d} (more details are provided in Supplementary Note S3).
 The method can accurately found the optimal point in the constraint-aware objective function.
@@
 The level set value $t_1$ and $t_2$ are limited in range from -0.5 to 0.5, which determine the volume fraction (i.e., relative density ) of a unit cell by thickening or thinning the surfaces.
-By varying the parameters $\alpha_1, \alpha_2, t_1, t_2$ in Eq.\ref{eq:4}, the TPMS structures can be adjusted, as illustrated in Fig\ref{fig:2}a.
+By varying the parameters $\alpha_1, \alpha_2, t_1, t_2$ in Eq.\ref{eq:17}, the TPMS structures can be adjusted, as illustrated in Fig.
+\ref{fig:3}.
 The merging operation not only produces geometric variations but also influences the mechanical properties of TPMS unit cells.
 
-We construct a rich database of TMPS unit cell by perturbing the parameters $\{\alpha_1, \alpha_2, t_1, t_2\} $ through Latin hyper-cube sampling (LHS) , resulting in 1372 unique structures (exclude some invalid structures).
+We construct a rich database of TMPS unit cell by perturbing the parameters $\{\alpha_1, \alpha_2, t_1, t_2\} $ through Latin hyper-cube sampling (LHS), resulting in 1372 unique structures (exclude some invalid structures).
 These structures exhibit orthotropic isotropic mechanical properties due to the cubic symmetric property of merged TPMS unit cell.
@@
 The mechanical properties of the cellular materials are influenced by both the scaffold architecture and the constituent materials.
-In the work, Ti6Al4V (Ti) was used as the constituent materials for orthopedic implants \citep{Peng2023} (material's parameters are provided in Supplementary S1).
+In the work, Ti6Al4V (Ti) was used as the constituent materials for orthopedic implants \citep{Peng2023} (material's parameters are provided in Supplementary Table S1).
 Ti alloy is bio-inert in human bodies and has been the de facto choice for 3D-printed orthopedic implants, achieving successful clinical applications in repairing bone defects.
-Figure \ref{fig:2}b shows the mechanical properties' distribution (effective elastic modulus $E$, Possion's ratio $v$) of G, D and Hybird TPMS unit cells (The mechanical properties of G and D were computed for an additional 100 samples, which are not included in the dataset of 1372 samples).
+Figure \ref{fig:2}b shows the mechanical properties' distribution (effective elastic modulus $E$, Possion's ratio $v$) of G, D and Hybird TPMS unit cells (The mechanical properties of G and D were computed for additional 100 samples, which are not included in the dataset of 1372 samples).
 The distributions of Possion's ratio of G and D exhibit single curve-like distributions with relative density and the Possion's ratio generally decrease as relative density increase, while hybrid TPMS unit cells exhibit significant broader property distribution.
-The relationship between effective elastic modulus $E$ and relative density $\rho$ follows an exponential form $E \propto E_s\rho^{n}$ (more details are provided in Supplementary S1), as founded in previous research \citep{Bauer2017}.
+The relationship between effective elastic modulus $E$ and relative density $\rho$ follows an exponential form $E \propto E_s\rho^{n}$ (more details are provided in Supplementary Note S1), as founded in previous research \citep{Bauer2017}.
 
@@
     \caption{\textbf{Overview of the} \textbf{structure variation and} \textbf{property} \textbf{distribution} \textbf{of merged TPMS unit cells}.
-\textbf{a} Examples of different merged TPMS unit cell’s structure are realized by varying the shape parameters $\alpha_1, \alpha_2,t_1,t_2$ of Gyroid (G) and Diamond (D).\textbf{ b }The Effective elastic modulus $E$, Possion’s ratio $v$ and relative density $\rho$ in dataset (plasma colormap).
+\textbf{a} Examples of different merged TPMS unit cell’s structure are realized by varying the shape parameters $\alpha_1, \alpha_2,t_1,t_2$ of Gyroid (G) and Diamond (D).\textbf{ b }The effective elastic modulus $E$, Possion’s ratio $v$ and relative density $\rho$ in dataset (plasma colormap).
 The size of markers is proportional to $E$.
 Property variation of G and D structures with the increasing $t_i( i=1,2,\Delta t = 0.01$) within $f_G$ and $f_D$, each with a size of 100 are evaluated separately for comparison (bone and viridis colormap, respectively).}
-    \label{fig:2}
+    \label{fig:3}
 \end{figure}
@@
 The database of hybrid TPMS unit cells is split with a ratio of 8:2 for training (1098) and testing (274), respectively.
-The coefficients $\alpha_1, \alpha_2$ of implicit function in database and the condition of elastic modulus $E$ are normalized before input to TPMS-GAN (more details are provided in Supplementary S4).
+The coefficients $\alpha_1, \alpha_2$ of implicit function in database and the condition of elastic modulus $E$ are normalized before input to TPMS-GAN (the architecture and hyper-parameters are provided in Table S5).
 We further improve the generative performance by ensuring the generated shape parameters can be accurately mapped back to their corresponding properties.
@@
 \end{equation}
-Figure \ref{fig:4} provides a schematic comparison between the navigator-free TPMS-WGAN and the navigator TPMS-WGAN  (the hyper-parameters and architecture are provided in Supplementary Table S2).
-As depicted in Figure \ref{fig:4}a, the training loss of the navigator-generator, represented by the blue line, is more stable than that of the navigator-free generator, indicated by the green line.
+Figure \ref{fig:4} provides a schematic comparison between the navigator-free TPMS-WGAN and the navigator TPMS-WGAN.
+As depicted in Fig.
+\ref{fig:4}\textbf{a}, the training loss of the navigator-generator, represented by the blue line, is more stable than that of the navigator-free generator, indicated by the green line.
 In WGAN, the discriminator's loss value serves as an indicator of model performance.
@@
 Next, we use t-SNE and kernel smoothing function estimate (KSFE) based on the structure parameters of TPMS unit cell for the 2D visualization of the test data.
-As illustrated in Fig \ref{fig:4}c, d, the data distribution generated by the navigator generator more closely resembles the distribution of the training data compared to that produced by the navigator-free generator.
+As illustrated in Fig.
+\ref{fig:4}\textbf{c, d}, the data distribution generated by the navigator generator more closely resembles the distribution of the training data compared to that produced by the navigator-free generator.
 To further assess the quality of the data generated by the navigator generator, we computed the Wasserstein distances \citep{Villani2008OptimalTO}.
-The results indicate a Wasserstein distance of \textbf{0.23} between the test data and the data generated by the navigator-free generator, and a distance of \textbf{0.34} between the test data and the data generated by the navigator generator.
-The diagonal plots of elastic modulus of test data and that evaluated of generated data of navigator-free generator and navigator generator via random forest model are shown in Fig \ref{fig:4}e, f (more details about random forest model as a surrogate model are provided in Supplementary S5).
+The results indicate a Wasserstein distance of \textbf{0.34} between the test data and the data generated by the navigator-free generator, and a distance of \textbf{0.23} between the test data and the data generated by the navigator generator.
+The diagonal plots of elastic modulus of test data and that evaluated of generated data of navigator-free generator and navigator generator via random forest (RF) model are shown in Fig \ref{fig:4}e, f (more details about RF model as a surrogate model are provided in Supplementary Note S5).
 The elastic modulus of the structure generated by the navigator generator aligns more closely with the test data's elastic modulus than that produced by the navigator-free generator, with coefficients of determination ($R^2$) of 0.982 and 0.706, respectively.
@@
 The continuous and low-dimensional latent space with generative cabilities is particularly advantageous for designing new structures by navigating this space through simple arithmetic operations on the latent representation $\boldsymbol{z}$.
-However, A general conditional WGAN lacks the ability to map a real structure to its latent space.
-To address the limitation, we trained an encoder, denoted as $IG_\psi$ to approximate inverse this mapping $(\boldsymbol{z},\boldsymbol{C})=IG_\psi(\boldsymbol{p})$.
-This inversion enables us to obtain a latent representation $\boldsymbol{z}$ from a real TPMS structure $\boldsymbol{p}$, facilitating exploration of the latent space through interpolation or variation.
+However, A conditional WGAN lacks the ability to map a real structure to its latent space.
+To address the limitation, we trained an encoder, denoted as $IG_\psi$ to approximate the inversed mapping $(\boldsymbol{z},\boldsymbol{C})=IG_\psi(\boldsymbol{p})$.
+This inversion enables us to obtain a latent representation $\boldsymbol{z}$ from a real TPMS structure $\boldsymbol{p}$, facilitating exploration of the latent space through interpolation or other variations.
 Although existing parameter-based and pixel/voxel-based generative models for cellular materials have successfully mapped topology and mechanical properties to a latent space using a similar data-driven design framework, they struggle to provide explainability in manipulating the geometry of TPMS unit cells via latent space or implicit function coefficients.
+Thus, we proposed an inversed TPMS-GAN (ITPMS-GAN).
 By integrating a TPMS-GAN, once the latent representation $\boldsymbol{z}$ is obtained, explicit geometric control can be applied to a structure through geometric conditions.
-We term this framework Inversed TPMS-GAN (ITPMS-GAN).
 In this approach, the parameters $\boldsymbol{p}$ of the TPMS structure are encoded into a latent space $\boldsymbol{z}'$, together with the edited geometry condition $\bar{\boldsymbol{s}}$, serve as input into a well-trained generator.
-The generator then produces the parameters $\boldsymbol{p}'$ of the TPMS structure.
+The generator then produces a new TPMS unit cell with parameters $\boldsymbol{p}'$.
 Our methodology involves training the inverse mapping encoder $IG_\psi$ after the TPMS-GAN has been trained.
-To train $IG_\psi$, we utilize the structure parameters $\boldsymbol{p}$ of the TPMS unit cell and the generated parameters $\boldsymbol{p}'$ from the TPMS-GAN, minimizing a squared reconstruction loss $\mathcal{L}_{IG}$ (Fig \ref{fig:5}a).
+To train $IG_\psi$, we utilize the structure parameters $\boldsymbol{p}$ of the TPMS unit cell and the generated parameters $\boldsymbol{p}'$ from the TPMS-GAN, minimizing a squared reconstruction loss $\mathcal{L}_{IG}$ (Fig.
+\ref{fig:5}\textbf{a}).
 \begin{equation}
@@
 \end{equation}
-where $m$ is batch size, and the detail hyperparamenters and architecture of ITPMS-GAN are provided in Supplementary Table S4.
+where $m$ is batch size (more details about ITPMS-GAN are shown in Table S4).
 A major advantage of ITPMS-GAN is its flexibility, allowing for explainable structural editing.
-As illustrated in Figure \ref{fig:5}b, the pore diameter of a TPMS unit cell from the test set can be edited using ITPMS-GAN.
-A TPMS unit cell, characterized by a relative density of\textbf{ 0.32 mm}, a pore diameter of \textbf{21 mm}, and a thickness of \textbf{14 mm}, is represented by a geometry vector $\boldsymbol{s}$ (Fig \ref{fig:5}b (iii)).
+As illustrated in Fig.
+\ref{fig:5}\textbf{b}, the pore diameter of a TPMS unit cell from the test set can be edited using ITPMS-GAN.
+A TPMS unit cell, characterized by a relative density of\textbf{ 0.32 mm}, a pore diameter of \textbf{21 mm}, and a thickness of \textbf{14 mm}, is represented by a geometry vector $\boldsymbol{s}$ (Fig \ref{fig:5}\textbf{b} (iii)).
 To adjust the pore diameter in $\boldsymbol{s}$ to 19 mm, 20 mm, 21 mm, 22 mm, and 23 mm, we first map the structure parameters $\boldsymbol{p}$ to the latent representation $\boldsymbol{z}'$.
-This latent representation, combined with the specified pore diameter as a condition, serves as input to $G_\phi^2$ (more details about $G^2_\phi$ are provided in Supplementary Table S3).
-The generated TPMS structures exhibit a gradual variation corresponding to the variations of pore diameter, as depicted in Fig \ref{fig:5}b.
-We conducted simulations to assess the geometric characteristics of the generated structures.
+This latent representation, combined with the specified pore diameter as a condition, serves as input to $G_\phi^2$ (more details about $G^2_\phi$ are provided in Table S3).
+The generated TPMS structures exhibit a gradual variation corresponding to the variations of pore diameter, as depicted in Fig.
+\ref{fig:5}\textbf{b}.
+We conducted simulations to assess the geometric features of the generated structures.
 The actual geometries closely matched the designed ones, except for pore diameters of 19 mm and 23 mm, which measured 18.5 mm and 24 mm, respectively.
-In the 2D t-SNE plot of the training dataset structures (Fig \ref{fig:5}c), the generated structures are visualized to assess their spatial distribution.
+In the 2D t-SNE plot of the training dataset structures (Fig.
+\ref{fig:5}c), the generated structures are visualized to assess their spatial distribution.
 The structure with a pore diameter of 19 mm is located on the boundary of the TPMS structure, with the design error primarily resulting from the limited data available in the training set, hindering the model's ability to learn its features.
 Furthermore, there is a significant discrepancy between the pre-set and validated pore diameters for 23 mm and 24 mm.
-Figure \ref{fig:5}c also reveals that the structure \textbf{v} is positioned far from other designed structures, forming a distinct D-like shape, and exhibits greater similarity to structure G.
+Figure \ref{fig:5}\textbf{c} also reveals that the structure \textbf{v} is positioned far from other designed structures, forming a distinct D-like shape, and exhibits greater similarity to structure G.
 The ITPMS-GAN model offers an explainable method for editing TPMS unit cells, instead of interpolation in latent space or adjusting implicit function coefficients.
@@
 In  the work, we employed the TPMS-GAN $G_\phi^1$ to generate 100,000 TPMS structures, forming a virtual design space $\Omega_E$ with a target elastic modulus of 6,000 MPa.
-As depicted in Figure \ref{fig:6}e, we compared the elastic modulus of these generated structures, as evaluated by a random forest model, with the pre-set value of 6,000 MPa (denoted by a red dashed line).
-The observed elastic modulus values ranged from 5,400 MPa to 6,300 MPa, clustering around the target modulus.
-To incorporate this target into constraint-aware active learning, we defined a constraint function based on the deviation of the generated structures' elastic modulus from the pre-set value of 6,000 MPa.
+As depicted in Fig.
+\ref{fig:6}\textbf{e}, we compared the elastic modulus of these generated structures, as evaluated by a RF model, with the pre-set value of 6,000 MPa (denoted by a red dashed line).
+The observed elastic modulus values ranged from 5,400 MPa to 6,300 MPa, clustering around the target elastic modulus.
+To incorporate this target into active learning process of yield strength, we defined a constraint function based on the deviation of the generated structures' elastic modulus from the pre-set value of 6,000 MPa.
 This function is expressed as:
@@
 The function $c(\boldsymbol{p}')$ reaches its maximum value when $E(\boldsymbol{p}') = 6000$.
-Figure \ref{fig:6}f illustrates the application of this constraint function within the virtual design space.
+Figure \ref{fig:6}\textbf{f} illustrates the application of this constraint function within the virtual design space.
 
@@
 
-\subsection{Develop high yield strength TPMS unit cells with matched elastic modulus via the constraint-Aware Strategy}
+\subsection{Develop high yield strength TPMS unit cells with matched elastic modulus via the constraint-aware strategy}
 
@@
 Calculating $\sigma_{ys}$ through simulation is resource-intensive due to the nonlinear plastic behavior of the constituent materials and the extensive number of discrete meshes involved.
-The yield strength calculation for each TPMS unit cell takes approximately 30 minutes, which is longer than the elastic modulus evaluation time of about 1 minute using FE simulation based on the numerical homogenization method (Details about computing platform are provided in Supplementary S6).
+The yield strength calculation for each TPMS unit cell takes approximately 30 minutes, which is longer than the elastic modulus evaluation time of about 1 minute using FE simulation based on the numerical homogenization method (details about computing platform are provided in Supplementary Note S6).
 BO method is efficiently to applied into expensive-to-evaluate black box problem.
 Here we propose an active learning approach to optimize yield strength while adhering to constraints on the elastic modulus.
-A support vector machine model is employed as the surrogate model, and bootstrap resampling is utilized to assess uncertainties by sampling the data with replacement.
+A support vector machine (SVM) model is employed as the surrogate model, and bootstrap resampling is utilized to assess uncertainties by sampling the data with replacement.
 In present study, we sampled 16 candidates from the virtual design space and evaluated their yield strength using FEM.
-This process was repeated 50 times, generating 50 resampled training sets to construct 50 support vector machine models.
+The training process of SVM was repeated 50 times, generating 50 resampled training sets to construct 50 SVM models.
 Consequently, each sample in the initial dataset yields 50 predicted values, which are used to determine the mean value ($\mu$) and the associated standard deviation ($\Sigma$).
@@
 
-The diagonal plot in Fig \ref{fig:7}a reveals that the model predictions are basically consistent with the observation values and the strategy of constraint-aware active learning recommended samples with high yield strength.
+The diagonal plot in Fig \ref{fig:7}\textbf{a} reveals that the model predictions are basically consistent with the observation values and the strategy of constraint-aware active learning recommended samples with high yield strength.
 We monitor mean square error (MSE) and R$^2$ as the surrogate model is successively refined with the results of evaluated TPMS structures  (Fig.
-\ref{fig:7}b).
+\ref{fig:7}\textbf{b}).
 
-The elastic modulus and yield strength of all recommended samples are presented in Fig \ref{fig:7}(d,e,f).
+The elastic modulus and yield strength of all recommended samples are presented in Fig.
+\ref{fig:7}(\textbf{d,e,f}).
 It is observed that the elastic modulus of these samples is closer to 6,000 MPa, with a mass center around 5,900 MPa, compared to the initial dataset, which has a mass center of approximately 5,800 MPa.
@@
 This metric effectively reflects the design performance of TPMS unit cell in achieving a matched implant scaffold with enhanced yield strength.
-
 Figure \ref{fig:7}g indicates that the optimal structure was identified at the 2nd iteration, with a $Y$ value of 1.72, significantly higher than the optimal value of 0.22 in initial dataset.
@@
 However, this approach led to improved performance at the 4th iteration.
-The stress-strain curve is depicted in Figure \ref{fig:7}i, while Figure \ref{fig:7}h presents the von Mises stress cloud plot.
+The stress-strain curve is depicted in Fig.
+\ref{fig:7}\textbf{i}, while Fig.
+\ref{fig:7}\textbf{h} presents the von Mises stress cloud plot.
 It is evident that stress concentration is localized at the junctions of unit cells.
-This study demonstrates that the constraint-aware active learning method successfully identified the optimal structure even beyond the training dataset, indicating a degree of extrapolation capability.
+This study demonstrates that the constraint-aware active learning method successfully identified the optimal performance of TPMS structure even beyond the training dataset, indicating a degree of extrapolation capability.
 Such robustness is particularly advantageous in clinical scenarios, where patient data, including target material properties and mechanical ranges, are often unknown in advance, and initial data distributions can vary widely.
 Furthermore, the design cost of TPMS unit cells with matched elastic modulus and high yield strength is significantly reduced by employing a method that requires the assessment of only 24 sample yield strengths.
-This is in stark contrast to the 1372 assessments needed in the one-step machine learning method used for training the generative model under bi-objective conditions.
+This is in stark contrast to the 1372 assessments needed in the one-step machine learning method used for training the generative model with bi-objective conditions.
 As a result, the design time is reduced about sixfold.
@@
 \textbf{h} The simulation strain-stress curves of the optimal structure recommended and the optimal
-structure in initial data. \textbf{g} The von Mises' stress cloud plot of the optimal structure recommended in active learning.}
+structure in initial data. \textbf{g} The von Mises stress cloud plot of the optimal structure recommended in active learning.}
     \label{fig:7}
@@
 
-In summary, this study proposes a data-efficient, two-stage bi-objective inverse design method for cellular materials based on TPMS.
-The method integrates a generative model, active learning, and finite element analysis, while accounting for the unbalanced costs associated with different objectives.
+In summary, this study proposes a data-efficient, two-stage bi-objective inverse design method for orthopedic implants based on TPMS.
+The method integrates a generative model, active learning, and finite element analysis, while accounting for the imbalanced costs associated with different objectives.
 Specifically, the methodology is applied to the inverse design of orthopedic implants.
@@
 The proposed TPMG-GAN, equipped with a navigator, generates TPMS unit cells under specified conditions, enabling the creation of a virtual structure space tailored to a target elastic modulus.
-Furthermore, an ITPMS-GAN was developed to design TPMS unit cell structures directly from geometric features in an explainable way, bypassing the need to interpolate in latent space or modify implicit function coefficients.
+Furthermore, an ITPMS-GAN was developed to design TPMS unit cell structures directly from geometric features in an explainable way, bypassing the need to interpolate in latent space or adjust implicit function coefficients.
 This approach not only diversifies the virtual structure space but also provides a novel pathway for TPMS structure design.
-Finally, a constraint-aware active learning framework was extended to optimize yield strength under elastic modulus constraints, achieving a significant performance improvement from 0.2 to 1.7 compared to the initial dataset.
+Finally, a constraint-aware active learning framework was extended to optimize yield strength under elastic modulus constraints, achieving a significant overall performance improvement from 0.2 to 1.7 compared to the initial dataset.
 This study demonstrates that the constraint-aware active learning method successfully identifies optimal structures even beyond the training dataset, showcasing its extrapolation capability.

### 2025-02-08 manuscript.tex
update on mac Feb 08 2025

@@
 \ead{tian0321@shu.edu.cn}
+\author[3]{Tong-Yi Zhang}
 \author[1,2]{Sheng Sun\corref{cor1}}
@@
 \begin{highlights}
-\item A TPMS-GAN with a navigator was developed to generate TPMS unit cells meeting specific mechanical and geometric conditions.
-\item An inversed TPMS-GAN was introduced to design TPMS unit cells directly from geometric features in an explainable way, bypassing the need to interpolate in latent space or adjust implicit function coefficients.
-\item A constraint-aware active learning method was proposed to tackle bi-objective optimization problems with imbalanced objective function costs.
+\item Developed a TPMS-GAN with a navigator to generate TPMS unit cells meeting specific mechanical and geometric conditions.
+\item Developed an inversed TPMS-GAN to design TPMS unit cells directly from geometric features in an explainable way, bypassing the need to interpolate in latent space or adjust implicit function coefficients.
+\item Proposed a constraint-aware active learning method to address bi-objective optimization problems with imbalanced objective function costs.
 \end{highlights}
@@
 Thus $\alpha_{\text{EI-C}}(\hat{\boldsymbol{x}})$ is the a standard EI of $\hat{\boldsymbol{x}}$ over the feasible point weighted by the probability that $\hat{\boldsymbol{x}}$ is feasible.
-In the work, we extend the constraint-aware expected improvement AF by surrogate $PF(\hat{\boldsymbol{x}})$ with the normalized distance between the constraint value $c(\hat{\boldsymbol{x}})$ and a target point $c^*$.
+In the work, we extend the constraint-aware expected improvement AF by replacing $PF(\hat{\boldsymbol{x}})$ with the normalized distance between the constraint value $c(\hat{\boldsymbol{x}})$ and a target point $c^*$.
 This distance is mathematically expressed as $ND(||c(\hat{\boldsymbol{x}})-c^*||)$.
-By incorporating the constraint function, the distribution of \(\alpha_{\text{EI}}(\hat{\boldsymbol{x}})\) is adjusted point-by-point.
+By incorporating the constraint function, the distribution of \(\alpha_{\text{EI}}(\hat{\boldsymbol{x}})\) is adjusted pointwisely.
 Notably, this approach eliminates the need to construct an additional probability model to surrogate the constraint function $c(\hat{\boldsymbol{x}}) $.
@@
 The mechanical properties of the cellular materials are influenced by both the scaffold architecture and the constituent materials.
-In the work, Ti6Al4V (Ti) was used as the constituent materials for orthopedic implants \citep{Peng2023} (material's parameters are provided in Supplementary Table S1).
+In the work, Ti6Al4V (Ti) was used as the constituent materials for orthopedic implants \citep{Peng2023} (material's parameters are provided in Table S1).
 Ti alloy is bio-inert in human bodies and has been the de facto choice for 3D-printed orthopedic implants, achieving successful clinical applications in repairing bone defects.

### 2025-03-12 manuscript.tex
update on mac

@@
 
-\title{Inverse design workflow of implicit surface-based cellular materials via conditional generative model and active learning}
+\title{Editable Design of Cellular Metamaterials via Conditional Generative Networks and Active Learning}
 
@@
 \author[3]{Bin Cao}
-\author[1]{Yuan Tian\corref{cor1}}
-\ead{tian0321@shu.edu.cn}
 \author[3]{Tong-Yi Zhang}
@@
 \begin{abstract}
-Implicit surface-based cellular materials have gained significant attention in bone scaffold applications due to their structural resemblance to natural bone.
-These materials exhibit excellent mechanical properties and bioadaptability, providing an ideal environment for bone tissue regeneration.
-However, the rational design of such materials often relies heavily on expert knowledge and extensive trial-and-error experiments.
-In the work, we propose a data-efficient, two-stage bi-objective optimization framework within a machine learning paradigm, which accounts for the disparate computational costs associated with different objectives.
-Specifically, we apply this methodology to the inverse design of orthopedic implants, integrating a generative model, active learning, and finite element analysis to achieve cellular materials with both biocompatible elastic modulus and enhanced yield strength.
-Our approach demonstrates significant improvements in overall performance compared to the initial dataset, while reducing design costs by approximately sixfold relative to conventional one-step bi-objective machine learning optimization methods.
-This framework establishes an efficient paradigm for the rapid and intelligent design of cellular materials with tailored mechanical properties, particularly in scenarios where objectives involve imbalanced computational costs.
+Implicit surface-based cellular metamaterials have garnered significant attention in bone scaffold applications due to their structural mimicry of natural bone, offering exceptional mechanical properties and bioadaptability for tissue regeneration.
+However, traditional design approaches for these metamaterials remain constrained by reliance on expert intuition and iterative trial-and-error processes, limiting their adaptability to diverse performance requirements.
+To address this, we propose an editable design framework leveraging conditional generative networks and active learning within a data-efficient, two-stage bi-objective optimization paradigm.
+This methodology explicitly addresses disparate computational costs between objectives—here applied to the inverse design of orthopedic implants—by integrating conditional generative networks for topology synthesis, active learning for targeted exploration of the design space, and finite element analysis for mechanical evaluation.
+The conditional generative networks enable explicit control over metamaterial geometry, while active learning minimizes costly simulations by prioritizing high-potential candidates.
+Compared to conventional bi-objective optimization methods, our approach achieves a sixfold reduction in computational expenses while significantly improving yield strength and biocompatible elastic modulus relative to baseline datasets.
+This framework establishes a paradigm for rapid, customizable design of cellular metamaterials with tailored mechanical properties, particularly in scenarios where objectives involve imbalanced computational effort.
+By unifying editable generative modeling with adaptive sampling, our work advances the intelligent and efficient development of metamaterials for applications demanding multifunctional performance.
 \end{abstract}
@@
 \begin{equation}
-\int_{\Omega}\hat{\varepsilon}^T:\mathbb{C}:\varepsilon^{*}d\Omega = \int_{\Omega}\hat{\varepsilon}^T:\mathbb{C}:\bar{\varepsilon}
+\int_{\Omega}\hat{\varepsilon}^T:\mathbb{C}:\varepsilon d\Omega = \int_{\Omega}\hat{\varepsilon}^T:\mathbb{C}^H:\bar{\varepsilon}d\Omega
 \label{eq:3}
@@
 Once $\varepsilon^{*}$ is obtained, the effective elastic tensor $\mathbb{C}^H$ can be determined using the following equation:
+% \begin{equation}
+% \mathbb{C}^H:\bar{\varepsilon} = \frac{1}{|\Omega|}\int_{\Omega}\mathbb{C}:(\bar{\varepsilon}+\varepsilon^{*})d\Omega
+%     \label{eq:4}
+% \end{equation}
+
 \begin{equation}
-\mathbb{C}^H:\bar{\varepsilon} = \frac{1}{|\Omega|}\int_{\Omega}\mathbb{C}:(\bar{\varepsilon}+\varepsilon^{*})d\Omega
-    \label{eq:4}
+    \mathbb{C}^H = \sum_{i=1}^m\frac{\Omega_e}{|\Omega|}\mathbb{C}(I-B\chi_e)
 \end{equation}
+
 where $|\Omega|$ denotes the volume of the unit cell.
 
-From the effective elastic tensor $\mathbb{C}^H$, the compliance tensor $\mathbb{S}^H$ can be derived, and its Voigt form is expressed as:
-\begin{equation}
-\mathbb{S}^H = \begin{bmatrix}
-\frac{1}{E_x} & -\frac{v_{yx}}{E_y} & -\frac{v_{zx}}{E_z} & 0 & 0 & 0 \\
--\frac{v_{xy}}{E_x} & \frac{1}{E_y} & -\frac{v_{zy}}{E_z} & 0 & 0 & 0 \\
--\frac{v_{xz}}{E_x} & -\frac{v_{yz}}{E_z} & \frac{1}{E_z} & 0 & 0 & 0 \\
-0 & 0 & 0 & \frac{1}{G_{yz}} & 0 & 0 \\
-0 & 0 & 0 & 0 & \frac{1}{G_{zx}} & 0 \\
-0 & 0 & 0 & 0 & 0 & \frac{1}{G_{xy}}
-\end{bmatrix}
-\label{eq:5}
-\end{equation}
-
-In this matrix, $E_i$ represents the elastic modulus along the $i^{\text{th}}$ direction, where $i \in \{x, y, z\}$.
-In the work, for cubic symmetric unit cells, we have effective elastic modulus $E^H=E_x=E_y=E_z$.
-Additionally, elastic modulus in other directions can be obtained from $\mathbb{S}^H$ using the following equation:
+Elastic modulus $E_i$, where $i \in \{x, y, z\}$, in different directions $(x,y,z)$  can be calculated using the following equation:
 \begin{equation}
@@
 \end{equation}
-Here, $E_{ijk}$ is the elastic modulus along the $[i,j,k]$ direction, and $\ell$ is the cosine of the angle between the orientation $[i,j,k]$ and the coordinate axes $[x, y, z]$.
+where $E_{ijk}$ is the elastic modulus along the $[i,j,k]$ direction, $\ell$ is the cosine of the angle between the orientation $[i,j,k]$ and the coordinate axes $[x, y, z]$, and $\mathbb{S}^H$ the compliance tensor with $\mathbb{S}^H = (\mathbb{C}^H)^{-1}$.
 This approach allows for the evaluation of elastic modulus in any orientation of the unit cell, facilitating the construction of a three-dimensional elastic modulus surface (see Fig S1).
@@
     \includegraphics[width=1\linewidth]{figures/3.pdf}        
-    \caption{\textbf{Generative modeling framework}.
-The conditional WGAN model can address multiple conditions including mechanical and geometric features of TPMS unit cell, here we called it TPMS-WGAN.
-Each condition can be turned on$/$off to meet various design requirements.
-Considering elastic modulus, the TPMS-WGAN takes effective elastic modulus $E$ and random noise $\boldsymbol{z} (\boldsymbol{z}\sim\mathcal{N}(\mathbf{0},\mathbf{I})$, a Gaussian distribution of zero mean and the identity as the covariance matrix) as input to generator $G_\phi^1$, and the generated TPMS structure (denoted by implicit function parameters $\boldsymbol{p}'$), $E$ and the real TPMS structure (denoted by $\boldsymbol{p}$) are then passed to the discriminator $D_\theta$ to output value $f_D$.
-The $\boldsymbol{p}'$ also is passed navigator $R_\omega$ to obtained the predicted effective elastic modulus $E'$.}
     \label{fig:2}
@@
 The ITPMS-GAN model offers an explainable method for editing TPMS unit cells, instead of interpolation in latent space or adjusting implicit function coefficients.
-The approach can be applied to diverse structures in virtual design space or create a more refined design space.
+The approach can be applied to diverse structures in virtual design space and create a more refined design space.
 
@@
 Here we propose an active learning approach to optimize yield strength while adhering to constraints on the elastic modulus.
-A support vector machine (SVM) model is employed as the surrogate model, and bootstrap resampling is utilized to assess uncertainties by sampling the data with replacement.
+A support vector regressor (SVR) model is employed as the surrogate model, and bootstrap resampling is utilized to assess uncertainties by sampling the data with replacement.
 In present study, we sampled 16 candidates from the virtual design space and evaluated their yield strength using FEM.
-The training process of SVM was repeated 50 times, generating 50 resampled training sets to construct 50 SVM models.
+The training process of SVM was repeated 50 times, generating 50 resampled training sets to construct 50 SVR models.
 Consequently, each sample in the initial dataset yields 50 predicted values, which are used to determine the mean value ($\mu$) and the associated standard deviation ($\Sigma$).
 
-Figure \ref{fig:7}c illustrates the transition of the query sample from the blue dot to the red dot at the 1st iteration, facilitated by the elastic modulus constraint-aware EI approach introduced in \ref{sec:2-4}.
+The diagonal plot in Fig \ref{fig:7}\textbf{a} reveals that the SVR model predictions are basically consistent with the observation values in intial dataset, which coefficient of determiantion $R^2$ and MSE are 0.94 and 0.28, respectively.
+Figure \ref{fig:7}\textbf{b }illustrates the transition of the query sample from the blue dot to the red dot at the 1st iteration, facilitated by the elastic modulus constraint-aware EI approach introduced in \ref{sec:2-4}.
 This shift indicates that the constraint function of the elastic modulus alters the maximum expected improvement over the best observed value in the training dataset.
@@
 
-The diagonal plot in Fig \ref{fig:7}\textbf{a} reveals that the model predictions are basically consistent with the observation values and the strategy of constraint-aware active learning recommended samples with high yield strength.
-We monitor mean square error (MSE) and R$^2$ as the surrogate model is successively refined with the results of evaluated TPMS structures  (Fig.
-\ref{fig:7}\textbf{b}).
+As illustrated in Fig\ref{fig:7}\textbf{c}, the SVR model exhibits significant performance fluctuations during iterative process.
+The $R^2$ metric undergoes a dramatic decrease from 0.94 to 0.71 during the first iteration, accompanied by a substantial increase in MSE from 0.28 to 5.19.
 
-The elastic modulus and yield strength of all recommended samples are presented in Fig.
-\ref{fig:7}(\textbf{d,e,f}).
-It is observed that the elastic modulus of these samples is closer to 6,000 MPa, with a mass center around 5,900 MPa, compared to the initial dataset, which has a mass center of approximately 5,800 MPa.
-Additionally, the yield strength of the recommended samples surpasses that of the initial dataset.
-To further demonstrate the efficacy of the constraint-aware active learning framework, the overall performance $Y$ of the TPMS unit cell is quantified by the following equation:
+The phenomenon arises from the enhancement of the elastic modulus-aware constraint of active learning extrapolation capability, which recommends samples with divergent distribution compared to the initial dataset, as shown in \ref{fig:7}\textbf{d}.
+During the first iteration, two samples exhibiting heterogeneous distributions compared to the initial dataset are selected through the elastic modulus-aware constraint and incorporated into the initial dataset.
+At this stage, the limited number of samples provides insufficient data for the SVR model to effectively capture extrapolation patterns in unexplored regions.
+Through successive iterations, however, the active learning approach progressively expands the dataset by recommending additional unknown areas of samples.
+This expansion enables the SVR model to continually refine its generalization ability, as evidenced by the gradual improvement of $R^2$ (to 0.94 and 0.97, 0.97 at the 2nd, 3rd, 4th, respectively) and reduction in MSE (to 2.02, 1.44, and 1.31 at the 2nd, 3rd, 4th, respectively).
 
+Figure \ref{fig:7}e illustrates the elastic modulus compatibility (EMC), defined by the absolute difference between 6000 MPa and the optimal elastic modulus in dataset.
+It can be observed that the EMC of recommended samples decrease from 279.76 MPa to 20.84 MPa while the yield strength (YS) increase from 148.19 MPa to 157.6 MPa after the first iteration, demonstrating the importance of the extrapolation in active learning framework.
+In successive iterations, EMC progressively decrease to 8.57 MPa and YS gradually increase to 159.91 MPa, indicating effective convergence toward optimal target.
+To futher demonstrate the efficiency of the elastic modulus-aware active learning framework, the comprehensive performance index (CPI) of the TPMS unit cell is quantified by the following equation:
 \begin{equation}
-    Y = Y_E^N+Y_{\sigma_{ys}}^N
-\label{eq:23}
+    \text{CPI} = \text{EMC}_\text{norm}+\text{YS}_\text{norm}
 \end{equation}
@@
     \begin{aligned}
-    Y_E^N &= \frac{Y_E-\text{min}(Y_E)}{\text{max}(Y_E)-\text{min}(Y_E)} 
- ,Y_E = \frac{1}{|E(\boldsymbol{p}')-E^*|}\\
-    Y^N_{\sigma_{ys}}& =\frac{Y_{\sigma_{ys}}-\text{min}(Y_{\sigma_{ys}})}{\text{max}(Y_{\sigma_{ys}})-\text{min}(Y_{\sigma_{ys}})} 
+        \text{EMC}_\text{norm} &= \frac{\text{EMC}_\text{max} - \text{EMC}}{\text{EMC}_\text{max} - \text{EMC}_\text{min}}\\
+        \text{YS}_\text{norm}&= \frac{\text{YS}-\text{YS}_\text{min}}{\text{YS}_\text{max} - \text{YS}_\text{min}}\\
     \end{aligned}
-\label{eq:24}
 \end{equation}
 
-This metric effectively reflects the design performance of TPMS unit cell in achieving a matched implant scaffold with enhanced yield strength.
-Figure \ref{fig:7}g indicates that the optimal structure was identified at the 2nd iteration, with a $Y$ value of 1.72, significantly higher than the optimal value of 0.22 in initial dataset.
-At the 3rd iteration, a decrease in overall performance was observed due to the active learning process, which integrates both exploration and exploitation capabilities.
-However, this approach led to improved performance at the 4th iteration.
-The stress-strain curve is depicted in Fig.
-\ref{fig:7}\textbf{i}, while Fig.
-\ref{fig:7}\textbf{h} presents the von Mises stress cloud plot.
+where $\text{EMC}_\text{max}$, $\text{EMC}_\text{min}$, $\text{YS}_\text{max}$, $\text{YS}_\text{min}$ were calculated using both the initial dataset and recommended samples.
+Within the initial dataset, the optimal values for $\text{EMC}_\text{norm}$ and $\text{YS}_\text{norm}$ were determined to be 0.22 and 0.67, respectively, resulting in an optimal CPI of 0.89.
+In the recommended samples, the CPI increased significantly to 2, indicating a substantial 124 \% improvement in performance compared to the initial dataset.
+
+The stress-strain curve and the von Mises stress cloud plot are depicted in Fig.
+\ref{fig:7}\textbf{f}.
 It is evident that stress concentration is localized at the junctions of unit cells.
@@
 Such robustness is particularly advantageous in clinical scenarios, where patient data, including target material properties and mechanical ranges, are often unknown in advance, and initial data distributions can vary widely.
-Furthermore, the design cost of TPMS unit cells with matched elastic modulus and high yield strength is significantly reduced by employing a method that requires the assessment of only 24 sample yield strengths.
+Furthermore, the design cost of TPMS unit cells with ompatibilitedelastic modulus and high yield strength is significantly reduced by employing a method that requires the assessment of only 24 sample yield strengths.
 This is in stark contrast to the 1372 assessments needed in the one-step machine learning method used for training the generative model with bi-objective conditions.
@@
 Bin Cao: Software, Investigation, Conceptualization, Formal analysis.
-Yuan Tian: Writing – review \& editing, Investigation, Formal analysis.
 Sheng Sun: Writing – review \& editing, Supervision, Funding acquisition, Formal analysis.

### 2025-03-12 others.tex
update on mac

\documentclass[preprint,review,12pt,authoryear]{elsarticle}

\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{titlesec} % 用于自定义章节标题样式
\usepackage{caption}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{hyperref}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}

\begin{document}
% \captionsetup[table]{
%   name={Table S},
%   labelformat=simple, % 使用简单的编号格式
%   labelsep=space,     % 编号和标题之间的分隔符为一个空格
%   justification=centering, % 居中对齐
% }

\begin{center}
\Large 
Motivation
\end{center}

\begin{center}
    Jiaxuan Ma ～～～～～～～～～～～ Email:mjx@shu.edu.cn
\end{center}

I am deeply motivated to contribute to this groundbreaking project that aims to revolutionize forging process optimization through AI-driven solutions. Below, I outline my key motivations for joining this initiative:

Creating a tool that can simulate forging processes in milliseconds, rather than hours, aligns perfectly with my research in accelerating simulation shape morphing of smart materials under mechanical-electrical coupling condition. I have developed U-LSTM and U-ViT models that can accelerate these simulations by four orders of magnitude while maintaining the high precision of FEM. Additionally, I introduced a data-based control framework for solving smart actuator underwater locomotion problems using deep reinforcement learning (DRL).

I also developed a visualization AI platform named \href{https://github.com/Jiaxuan-Ma/MLMD}{MLMD} for material performance prediction and design. This platform includes data analysis, property prediction, transfer learning, surrogate optimization and active learning. It offers a web-based, user-friendly interface that requires no programming and can be accessed anywhere, anytime. Furthermore, I have researched mechanical meta-material design through implicit-based functions and developed TPMS-GAN for real-time, multi-objective design, considering the costs associated with each objective.

In summary, I am inspired by the opportunity to apply my skills and knowledge to a project that has the potential to transform the forging industry. This project aligns with my career aspirations and personal values, and I am excited to be part of a team that is shaping the future of manufacturing.

%% If you have bibdatabase file and want bibtex to generate the
%% bibitems, please use
%%
% \bibliographystyle{elsarticle-harv} 
% \bibliography{refs}

%% else use the following coding to input the bibitems directly in the
%% TeX file.

% \begin{thebibliography}{00}

% %% \bibitem[Author(year)]{label}
% %% Text of bibliographic item

% \bibitem[ ()]{}

% \end{thebibliography}
\end{document}

\endinput
%%
%% End of file `elsarticle-template-harv.tex'.

### 2025-03-12 refined_manuscript.tex
update on mac

%% Copyright 2007-2020 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%% 
%% Template article for Elsevier's document class `elsarticle'
%% with harvard style bibliographic references
\documentclass[preprint,review,12pt,authoryear]{elsarticle}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{caption}
\usepackage[margin=1cm]{geometry}
\journal{Journal of the Mechanics and Physics of Solids}
\begin{document}
\captionsetup[figure]{name={\textbf{Fig.}},labelsep=period} 
\begin{frontmatter}
\title{Inverse design workflow of implicit surface-based cellular materials via conditional generative model and active learning}

\author[1]{Jiaxuan Ma}
\author[3]{Bin Cao}
\author[1]{Yuan Tian}
%\ead{tian0321@shu.edu.cn}
%\author[1]{Yuan Tian\corref{cor1}}
%\ead{tian0321@shu.edu.cn}
\author[3]{Tong-Yi Zhang}
\author[1,2]{Sheng Sun\corref{cor1}}
\ead{mgissh@t.shu.edu.cn}

\address[1]{Materials Genome Institute, Shanghai University, Shanghai, 200444, China}
\address[2]{Shanghai Frontier Science Center of Mechanoinformatics, Shanghai University, Shanghai, 200444, China}
\address[3]{Advanced Materials Thrust, Hong Kong University of Science and Technology (Guangzhou), Guangzhou, 511400, Guangdong, China}

\cortext[cor1]{Corresponding author}

\begin{abstract}
Implicit surface-based cellular materials have attracted considerable interest for bone scaffold applications owing to their structural similarity with natural bone. These materials demonstrate superior mechanical properties and bioadaptability, creating an optimal environment for bone tissue regeneration. However, the rational design of such materials frequently depends on expert knowledge and extensive trial-and-error experimentation. In this study, we present a data-efficient two-stage bi-objective optimization framework within a machine learning paradigm that addresses disparate computational costs between objectives. Applying this methodology to orthopedic implant inverse design, we integrate generative modeling, active learning, and finite element analysis to achieve cellular materials with both biocompatible elastic modulus and enhanced yield strength. Our approach demonstrates substantial performance improvements compared to initial datasets while reducing design costs by approximately sixfold relative to conventional single-step bi-objective optimization methods. This framework establishes an efficient paradigm for rapid intelligent design of cellular materials with tailored mechanical properties, particularly when addressing objectives involving imbalanced computational expenses.
\end{abstract}

\begin{graphicalabstract}
%\includegraphics{grabs}
\end{graphicalabstract}

\begin{highlights}
\item Developed TPMS-GAN with navigator architecture to generate TPMS unit cells satisfying specific mechanical and geometric constraints
\item Created inverse TPMS-GAN for direct design of TPMS unit cells from geometric features, bypassing latent space interpolation or implicit function coefficient adjustment
\item Proposed constraint-aware active learning method to solve bi-objective optimization problems involving objectives with imbalanced computational costs
\end{highlights}

\begin{keyword}
Multi-objective optimization \sep Cellular structure design \sep Generative adversarial network \sep Constraint-aware active learning
\end{keyword}
\end{frontmatter}

\section{Introduction}
Cellular materials have become ubiquitous in engineering applications owing to their exceptional mechanical properties and adaptable characteristics, including lightweight structures \citep{Schaedler2011, Berger2017, Han2015, Tancogne-Dejean2018}, thermal insulation \citep{Li2021d}, acoustic performance \citep{Sekar2024}, and tissue engineering suitability \citep{Li2024c,Peng2023,Tabrizian2024}. The advent of additive manufacturing (AM) has further revolutionized their production by enabling cost-effective fabrication of complex, customized structures. However, despite their broad applicability and potential, the design process for cellular materials remains particularly challenging.

Traditional design methodologies typically employ nature-inspired architectures \citep{Fernandes2021,Bandyopadhyay2021,Sethi2023}, human intuition \citep{Schaedler2011,Berger2017,Xu2016a}, and numerical simulations such as topology optimization \citep{Andersen2019,Bendsoe1999,Collet2018}, spinodal separation \citep{Hsieh2019,Roding2022}, or Gaussian random fields \citep{Kumar2020,Zheng2020abc}. These rule-based approaches are often laborious and time-consuming, with design performance heavily dependent on the designer's expertise.

The emergence of artificial intelligence (AI) has transformed cellular material design paradigms through machine learning. By extracting non-linear relationships between geometric features and mechanical properties from data, trained models can serve as cost-effective surrogates for expensive simulations and experiments. This capability enables seamless integration into heuristic algorithms for optimizing structures with target properties like elastic modulus \citep{Garland2021,Lee2022,Chen2024b}, bulk resistance \citep{Liu2020a}, and stress-strain behavior \citep{Deng2022a,Ma2020b}. However, surrogate optimization requires multiple model invocations, posing challenges for global optimization and real-time design applications.

Generative models including variational auto-encoders (VAE) \citep{Wang2020a,Zheng2023}, generative adversarial networks (GAN) \citep{Nie2020,Shen2022,Kim2020b}, and diffusion models \citep{Bastek2023,Maze2022,Vlassis2023} have demonstrated remarkable potential in cellular material design. These systems learn structural distributions from training data to generate novel configurations. Conditional generative models prove particularly valuable for inverse design challenges where multiple structures correspond to single property targets. Nevertheless, dataset construction costs remain underaddressed, especially in multi-objective scenarios where disparate evaluation costs exist between objectives - a common occurrence when designing cellular structures requiring simultaneous optimization of linear and nonlinear mechanical properties.

Triply periodic minimal surfaces (TPMS), derived from implicit functions with controllable unit cell geometries through coefficient adjustment \citep{Ma2020a}, represent an important class of cellular materials. Characterized by locally symmetric saddle shapes with vanishing mean curvature and non-positive Gaussian curvature, TPMS domains form single connected components without sealed cavities \citep{Kapfer2011}. These geometric properties make them ideal for orthopedic implants where bone-like elastic modulus matching minimizes stress shielding while maximizing yield stress ensures mechanical support and fatigue resistance. Although numerical homogenization efficiently evaluates TPMS elastic modulus, nonlinear plasticity analysis via finite element methods (FEM) incurs substantial computational costs for yield stress determination.

This work presents a two-step strategy combining generative modeling with active learning to address bi-objective TPMS unit cell design involving imbalanced property evaluation costs. As illustrated in Fig \ref{fig:1}, our methodology comprises three components: (1) Generation of structures with target elastic modulus using a trained TPMS-GAN model, creating a virtual design space ($\Omega_E$); (2) Development of an inverse TPMS-GAN (ITPMS-GAN) for latent space exploration and direct geometric manipulation; (3) Elastic modulus-constrained active learning for yield strength optimization. Initial FEM evaluation establishes the dataset, followed by Bayesian optimization (BO)-based active learning \citep{Ma2024b,Cao2024a,Tian2024a} to maximize yield strength within $\Omega_E$. This cohesive workflow seamlessly integrates generative exploration with targeted optimization, enabling the efficient discovery of high-performance TPMS unit cell designs while mitigating computational bottlenecks posed by imbalanced property evaluations.

\begin{figure}
    \centering
    \includegraphics[width=1\linewidth]{figures/1.pdf}
    \caption{\textbf{An overview of the proposed workflow for TPMS unit cells design.} (a) The generator in the TPMS-GAN model produces virtual design space ($\Omega_E$) with desired elastic modulus. (b) The ITPMS-GAN model edits TPMS structures through geometric features to enhance candidate diversity in $\Omega_E$. (c) A machine learning algorithm interactively queries finite element simulations to discover new TPMS designs with high yield strength and target elastic modulus via constrained active learning in $\Omega_E$.}
    \label{fig:1}
\end{figure}

\section{Models and methods}
\subsection{TPMS-based cellular structures}
TPMS can be generated using a level-set approximation equation expressed as a sum of Fourier series terms [xxx]:
\begin{equation}
 \Psi(\boldsymbol{r})=\sum_kF(\boldsymbol{k})\cos\left([2\pi \boldsymbol{k}\cdot \boldsymbol{r}-\alpha(\boldsymbol{k})]\right)=0
\label{eq:1}
\end{equation}
where $\boldsymbol{k}$ represents the reciprocal vector, $\alpha(\boldsymbol{k})$ denotes a phase shift, and $F(\boldsymbol{k})$ corresponds to the amplitude associated with the given $\boldsymbol{k}$ vector. When truncated to the leading term, this series produces a function $\phi$ composed of trigonometric combinations satisfying $\phi(\boldsymbol{r})=\phi(x,y,z)=c$. The surface defined by $\phi(x, y, z)$ at isovalue $c$ exhibits topological similarity to minimal surfaces.

\subsection{Effective properties of homogenized cellular structures}
\label{subsec:homo}
This study employs a voxel-based asymptotic homogenization method \citep{Dong2019} to calculate the effective elastic tensor of TPMS unit cells. The method assumes physical quantities like stress and strain depend on both macroscale ($X$) and microscale ($x/\varepsilon$), where $\varepsilon$ represents the scale factor. These quantities are homogenized at the macroscale while maintaining periodicity at the microscale. By asymptotically expanding the microscopic strain tensor and neglecting higher-order terms, we obtain:
\begin{equation}
    \varepsilon = \bar{\varepsilon} + \varepsilon^{*}
\label{eq:2}
\end{equation}
Here, $\bar{\varepsilon}$ signifies macroscopic mean strain within the unit cell, while $\varepsilon^{*}$ indicates periodic microscale perturbation strain. The perturbation strain is obtained by solving the mechanical balance equation:
\begin{equation}
\int_{\Omega}\hat{\varepsilon}^T:\mathbb{C}:\varepsilon^{*}d\Omega = \int_{\Omega}\hat{\varepsilon}^T:\mathbb{C}:\bar{\varepsilon}d\Omega
\label{eq:3}
\end{equation}
where $\hat{\varepsilon}$ represents virtual strain, $\mathbb{C}$ the material elastic tensor, and $\Omega$ the unit cell domain. This equation is numerically discretized using finite element analysis with eight-node hexahedrons, voxelizing each unit cell into $40 \times 40 \times 40$ cubes (Fig S1). Following determination of $\varepsilon^{*}$, the effective elastic tensor $\mathbb{C}^H$ becomes:
\begin{equation}
\mathbb{C}^H:\bar{\varepsilon} = \frac{1}{|\Omega|}\int_{\Omega}\mathbb{C}:(\bar{\varepsilon}+\varepsilon^{*})d\Omega
    \label{eq:4}
\end{equation}
where $|\Omega|$ denotes unit cell volume.

Elastic modulus $E_{ijk}$ along the $[i,j,k]$ direction can be calculated using the following equation:
\begin{equation}
\frac{1}{E_{ijk}} = \mathbb{S}^H_{11} - 2 \left(\mathbb{S}^H_{11} - \mathbb{S}^H_{12} - \frac{1}{2} \mathbb{S}^H_{44} \right) \times \left( \ell_{i1}^2 \ell_{j2}^2 + \ell_{j2}^2 \ell_{k3}^2 + \ell_{i1}^2 \ell_{k3}^2 \right),
    \label{eq:6}
\end{equation}

where $\ell$ is the cosine of the angle between the orientation $[i,j,k]$ and the coordinate axes $[x, y, z]$, and $\mathbb{S}^H$ the compliance tensor with $\mathbb{S}^H = (\mathbb{C}^H)^{-1}$.  This formulation enables graphical representations of the variation in the magnitude of $E_{ijk}$ with respect to the crystallographic axes (Fig S1).

\subsection{The architecture of TPMS-WGAN model}
In this work, we implement a conditional Wasserstein GAN consisting of four key components: a generator network ($G_\phi$), a discriminator network ($D_\theta$), a navigator network ($R_\omega$), and a condition module $\boldsymbol{C}$ incorporating mechanical properties and geometric features of the TPMS unit cell. Individual conditions can be selectively activated or deactivated during training to accommodate diverse design requirements (Fig. \ref{fig:2}). The generator $G_\phi$, parameterized by trainable weights $\phi$, transforms Gaussian noise ($\boldsymbol{z}$) and conditional inputs into TPMS structural parameters $\boldsymbol{p} \in \mathbb{R}^4$, producing synthetic outputs $\boldsymbol{p}'$. Simultaneously, the discriminator $D_\theta$ with parameters $\theta$ evaluates the authenticity of input parameter sets. It accepts real data $\boldsymbol{p}$, generated samples $\boldsymbol{p}'$, and conditional inputs $\boldsymbol{C}$, outputting a scalar value $D_\theta(\boldsymbol{p}'|\boldsymbol{C})$ that quantifies the realism of generated parameters.

The adversarial training process establishes a two-player minimax game between generator and discriminator, formalized by the loss function:

\begin{equation}
\mathcal{L}_{(G_\phi, D_\theta)}= \min_G \max_{D} \mathbb{E}_{\boldsymbol{p} \sim \mathbb{P}_r} \left[ D_\theta(\boldsymbol{p}|\boldsymbol{C}) \right] - \mathbb{E}_{\boldsymbol{p}' \sim \mathbb{P}_g} \left[ D_\theta (\boldsymbol{p}') \right]
\label{eq:7}
\end{equation}

where $D$ represents 1-Lipschitz functions, $\mathbb{P}_r$ denotes the data distribution, and $\mathbb{P}_g$ corresponds to the implicit model distribution defined by $\boldsymbol{p}'=G_\phi(\boldsymbol{z}|\boldsymbol{C})$. To stabilize training dynamics and address gradient-related challenges, we implement Wasserstein GAN with gradient penalty (WGAN-GP) \citep{Gulrajani2017}.

\begin{figure}
    \centering
    \includegraphics[width=1\linewidth]{figures/3.pdf}        
    \caption{\textbf{Generative modeling framework}. Our conditional WGAN architecture, termed TPMS-WGAN, integrates multiple mechanical and geometric conditions for TPMS unit cell design. Conditions can be independently toggled during training. For elastic modulus integration, the model combines effective modulus $E$ with Gaussian noise $\boldsymbol{z} (\boldsymbol{z}\sim\mathcal{N}(\mathbf{0},\mathbf{I}))$ as generator inputs. The synthesized structural parameters $\boldsymbol{p}'$, along with real data $\boldsymbol{p}$ and modulus $E$, are fed to the discriminator for realism assessment ($f_D$). Concurrently, generated parameters undergo navigator network processing to predict elastic modulus $E'$.}
    \label{fig:2}
\end{figure}

\subsection{Constraint-aware active learning}
\label{sec:2-4}
Bayesian optimization (BO)-based active learning methods excel in solving computationally expensive black-box problems. Unlike gradient-based or heuristic approaches that rely solely on surrogate model predictions, BO leverages probabilistic estimates from sequentially updated surrogate models. The framework comprises two core elements:
\begin{itemize}
    \item A surrogate model enabling efficient exploration of virtual design spaces with uncertainty quantification
    \item An acquisition function (AF) balancing exploration and exploitation to score candidate samples
\end{itemize}

We employ support vector machines (SVM) as surrogates for expensive finite element simulations of TPMS yield strength. Bootstrap methods introduce prediction uncertainties, constructing the probabilistic model:
$$
y=f(\boldsymbol{x})+\varepsilon,\quad \varepsilon\sim(0, \Sigma^2)
$$
This model estimates mean predictions $f(\boldsymbol{x})$ and associated uncertainties $\Sigma^2$ across unexplored design spaces.

BO operates through iterative optimization cycles. At each iteration:
\begin{enumerate}
    \item SVM evaluates all unobserved samples in $\Omega_E$
    \item AF selects optimal candidate $\hat{\boldsymbol{x}}^*$ for simulation/experimentation
    \item New data pair $(\hat{\boldsymbol{x}}^*, f(\hat{\boldsymbol{x}}^*))$ augments dataset $\mathcal{D} = \{(\boldsymbol{x}_1, f(\boldsymbol{x}_1)), \ldots, (\boldsymbol{x}_n, f(\boldsymbol{x}_n))\}$
    \item SVM updates to improve predictive accuracy
\end{enumerate}

The process iterates until meeting convergence criteria or budget limits. Central to this approach is AF-driven candidate selection via expected utility maximization:

\begin{equation}
\alpha(\boldsymbol{x}) = \mathbb{E}[I(\boldsymbol{x})|\mathcal{D}]
\label{eq:8}
\end{equation}

Using the prevalent Expected Improvement (EI) utility function:
\begin{equation}
I_\text{EI}(\boldsymbol{x})=\max(f(\hat{\boldsymbol{x}})-f^*, 0)
\label{eq:9}    
\end{equation}

Substituting into Eq. \ref{eq:8} and applying reparameterization yields:
\begin{equation}
\alpha_\text{EI}(\boldsymbol{x}) = \left(\mu(\boldsymbol{x}) - f^*\right) \Phi\left(\frac{\mu(\boldsymbol{x}) - f^*}{\Sigma(\boldsymbol{x})}\right) + \Sigma(\boldsymbol{x}) \phi\left(\frac{\mu(\boldsymbol{x}) - f^*}{\Sigma(\boldsymbol{x})}\right)
\label{eq:10}    
\end{equation}

where $\phi(\cdot)$ denotes the probability density function (PDF) and $\Phi(z)$ represents the cumulative distribution function (CDF) of the standard normal random variable $z$. The right-hand side consists of two components: the first term governs exploitation, while the second facilitates exploration. The acquisition function evaluates unknown samples in the virtual design space to identify potential candidates for subsequent simulations or experiments.

The incorporation of inequality constraints into Bayesian optimization can be formulated as:
\begin{equation}
\max_{c(\boldsymbol{x}) \leq \lambda} f(\boldsymbol{x})
\label{eq:11}
\end{equation}
where $c(\boldsymbol{x})$ represents additional outputs from dataset $\mathcal{D}$, modeled independently through a probabilistic framework analogous to $f(\cdot)$. The constraint $c(\boldsymbol{x})\leq \lambda$ defines the feasible region within the virtual design space. The constrained expected improvement for candidate $\hat{\boldsymbol{x}}$ is expressed as:
\begin{equation}
I_{\text{EI-C}}(\hat{\boldsymbol{x}})=\Delta_\text{C}(\hat{\boldsymbol{x}})\max\{0, f(\hat{\boldsymbol{x}})-f^*\}=\Delta_\text{C}(\hat{\boldsymbol{x}})I_{\text{EI}}(\hat{\boldsymbol{x}})
    \label{eq:12}
\end{equation}
where $\Delta_\text{C}(\hat{\boldsymbol{x}})\in \{0,1\}$ serves as a feasibility indicator, equaling 1 if $c(\hat{\boldsymbol{x}})\leq \lambda$ and 0 otherwise. This binary random variable follows a Bernoulli distribution:
\begin{equation}
    PF(\hat{\boldsymbol{x}}):=Pr[c(\boldsymbol{x})\leq \lambda] 
    \label{eq:13}
\end{equation}
Here, $PF(\hat{\boldsymbol{x}})$ corresponds to the cumulative distribution function. These derivations culminate in the constrained expected improvement acquisition function:
\begin{equation}
\begin{aligned}
\alpha_{\text{EI-C}}(\hat{\boldsymbol{x}}) &=\mathbb{E}[I_\text{EI-C}(\hat{\boldsymbol{x}})]\\
&= \mathbb{E}[\Delta_{C}(\hat{\boldsymbol{x}})I_{\text{EI}}(\hat{\boldsymbol{x}})|\hat{\boldsymbol{x}}]\\
&= \mathbb{E}[\Delta_{C}(\hat{\boldsymbol{x}})|\hat{\boldsymbol{x}}]\mathbb{E}[I_\text{EI}(\hat{\boldsymbol{x}})|\hat{\boldsymbol{x}}]\\
&=PF(\hat{\boldsymbol{x}})\alpha_{\text{EI}}(\hat{\boldsymbol{x}})
\end{aligned}
\label{eq:14}
\end{equation}

Thus, $\alpha_{\text{EI-C}}(\hat{\boldsymbol{x}})$ represents the standard expected improvement weighted by the feasibility probability of $\hat{\boldsymbol{x}}$. In our methodology, we substitute $PF(\hat{\boldsymbol{x}})$ with a normalized distance metric between constraint value $c(\hat{\boldsymbol{x}})$ and target point $c^*$, denoted as $ND(||c(\hat{\boldsymbol{x}})-c^*||)$. This modification adaptively adjusts the distribution of $\alpha_{\text{EI}}(\hat{\boldsymbol{x}})$ without requiring additional probabilistic modeling for constraints. Consequently, Equation \ref{eq:14} transforms into:
$\alpha_{\text{EI-C}}(\hat{\boldsymbol{x}}) =ND(||c(\hat{\boldsymbol{x}})-c^*||)\alpha_{\text{EI}}(\hat{\boldsymbol{x}})$.

Figure \ref{fig:6} contrasts constraint-unaware and constraint-aware active learning processes. The blue dot in Fig. \ref{fig:6}\textbf{a} marks the optimum for the unconstrained objective function, while the red dot in Fig. \ref{fig:6}\textbf{b} indicates the constrained counterpart. Our normalized constraint function modifies EI scores across the virtual data space, evident in the shifted query points from Fig. \ref{fig:6}\textbf{c} to \ref{fig:6}\textbf{d} (see Supplementary Note S3). This approach successfully identifies optimal points under constraints and influences subsequent query selection through exploitation-exploration balance adjustments.

\section{Results and Discussions}
\subsection{Database of TPMS-based cellular structures}

Schoen's gyroid (G) and diamond (D) TPMS configurations exhibit remarkable geometric versatility with an exceptionally broad elastic modulus range \citep{Lee2016}. Their implicit functions $f(x,y,z)$ are defined as:

\begin{equation}
\begin{aligned}
f_G(x,y,z)&= \cos(2\pi y)\sin(2\pi x)+\cos(2\pi x)\sin(2\pi z)\\&+\cos(2\pi z)\sin(2\pi y)+t_1 = 0, t_1 =0
\end{aligned}
\label{eq:15}
\end{equation}
\begin{equation}
\begin{aligned}
f_D(x,y,z)&=\cos(2\pi x)\cos(2\pi y)\cos(2\pi z)\\&-\sin(2\pi x)\sin(2\pi y)\sin(2\pi z)+t_2=0, t_2 =0
\end{aligned}
\label{eq:16}
\end{equation}

Beyond their compact representations, TPMS-based units can be diversified through function combinations and coefficient adjustments \citep{Wang2019b}. Our hybrid structures combine G and D configurations via weighted implicit functions:
\begin{equation}
\begin{aligned}
    f_{Hybrid}(x, y, z) &=\alpha_1 (4f_G(x,y,z))+\alpha_2(4f_D(x, y,z ))\\
    \alpha_1+\alpha_2 &= 1,
    0\leq\alpha_1, \alpha_2 \leq1,
\end{aligned}
\label{eq:17}
\end{equation}

Parameters $\alpha_1$ and $\alpha_2$ vary stochastically while maintaining unit summation to generate structural diversity. Level set values  {不一致}{$t_1$ and $t_2$}, constrained within [-0.5, 0.5], control volume fractions through surface thickness modulation. Variations in $\alpha_1, \alpha_2, t_1,$ and $t_2$ (Eq.\ref{eq:17}) produce distinct TPMS architectures as depicted in Fig. \ref{fig:3}. These amalgamations induce both geometric variations and mechanical property modifications in TPMS unit cells.

We constructed a comprehensive database of TPMS unit cells by perturbing parameters $\{\alpha_1, \alpha_2, t_1, t_2\}$ through Latin hypercube sampling (LHS), generating 1372 unique structures after excluding invalid configurations. These structures demonstrate isotropic mechanical properties arising from the cubic symmetry inherent to merged TPMS unit cells. For each structure, we calculated the effective mechanical stiffness tensor using numerical homogenization methods as described in Section \ref{subsec:homo}. The mechanical behavior of cellular materials depends on both scaffold architecture and constituent material properties.

Ti6Al4V (Ti) alloy was selected as the constituent material for orthopedic implants \citep{Peng2023}, with material parameters detailed in Table S1. Widely adopted for 3D-printed bone defect repairs, this bio-inert Ti alloy has achieved clinical success in medical applications. Figure \ref{fig:2}b illustrates the distributions of effective elastic modulus ($E$) and Poisson's ratio ($v$) for G, D, and hybrid TPMS unit cells. Notably, we evaluated an additional 100 samples for G and D structures beyond the primary dataset. The Poisson's ratio distributions for G and D exhibit single-curve patterns inversely correlated with relative density, while hybrid TPMS configurations show broader property variations.

The relationship between effective elastic modulus $E$ and relative density $\rho$ follows the exponential form:
$$E \propto E_s\rho^{n}$$
as established in prior research \citep{Bauer2017}, with additional details provided in Supplementary Note S1.

\begin{figure}
    \centering
    \includegraphics[width=0.75\linewidth]{figures/2.pdf}
    \caption{\textbf{Structural variations and property distributions of merged TPMS unit cells}. \textbf{a} Representative structures generated by varying shape parameters $\alpha_1, \alpha_2,t_1,t_2$ for Gyroid (G) and Diamond (D). \textbf{b} Dataset visualization of effective elastic modulus $E$, Poisson's ratio $v$, and relative density $\rho$ using plasma colormap. Marker sizes correlate with $E$. Property variations for G and D structures were evaluated through incremental $t_i( i=1,2,\Delta t = 0.01$) adjustments within $f_G$ and $f_D$, each analyzed across 100 samples (represented by bone and viridis colormaps).}
    \label{fig:3}
\end{figure}

\subsection{Performance of TPMS-WGAN}
To train the TPMS-GAN for generating virtual designs with target elastic moduli, we implemented conditional training focused on $E$ while disabling other constraints. The hybrid TPMS dataset was partitioned into 1098 training and 274 testing samples (8:2 ratio). Input parameters $\alpha_1, \alpha_2$, and $E$ were normalized prior to network input, with architecture details provided in Table S5.

We enhanced generative performance by ensuring accurate parameter-to-property mapping through a dedicated property navigator $R_\omega$. This introduced an additional loss term:
\begin{equation}
\mathcal{L}_{(R_\omega)}=\mathbb{E}_{\boldsymbol{p}' \sim \mathbb{P}_g}(|R_\omega(\boldsymbol{p}')-E|)
\label{eq:18}
\end{equation}

The combined discriminator loss becomes:
\begin{equation}
\mathcal{L}_{D_\theta} =  \mathcal{L}_{(G_\phi, D_\theta)} + \eta *\mathcal{L}_{R_\omega}
\label{eq:19}
\end{equation}
where $\eta=0.5$, with generator loss defined as:
\begin{equation}
\mathcal{L}_{G_\phi} =  - \mathbb{E}_{\boldsymbol{z}\sim \mathcal{N}(\boldsymbol{0},\boldsymbol{I})} \left[ D_\theta (G_\phi(\boldsymbol{z}|\boldsymbol{C})\right]
\label{eq:20}
\end{equation}

Figure \ref{fig:4} compares navigator-free and navigator-enhanced TPMS-WGAN architectures. The navigator generator demonstrates superior training stability (blue vs green curves in Fig. \ref{fig:4}a) with lower discriminator losses (2.57 vs 3.12). t-SNE and KSFE visualizations (Fig. \ref{fig:4}c,d) reveal closer alignment between navigator-generated data and training distributions.

Wasserstein distance calculations \citep{Villani2008OptimalTO} quantify this improvement, showing distances of 0.34 (navigator-free) versus 0.23 (navigator-enhanced). Random forest evaluations (Fig. \ref{fig:4}e,f) demonstrate enhanced agreement between generated and test data elastic moduli ($R^2=0.982$ vs $0.706$), confirming the navigator's effectiveness in guiding gradient descent during training.

\begin{figure}
    \centering
    \includegraphics[width=0.75\linewidth]{figures/4.pdf}
    \caption{\textbf{Evaluation of the TPMS-GAN model.} (\textbf{a}) Loss values for the navigator-free generator (green) and navigator generator (blue) during training. (\textbf{b}) Loss values for the navigator-free discriminator (orange) and navigator discriminator (red). 2D t-SNE plots show data distributions: training data (viridis colormap) versus generated data (plasma colormap) under corresponding elastic moduli for navigator-free generator (\textbf{c}) and navigator generator (\textbf{d}). Density represents probability per unit area. Conditional vs evaluated elastic moduli comparisons for structures from the navigator-free generator (\textbf{e}) and navigator generator (\textbf{f}).}
    \label{fig:4}
\end{figure}

The continuous, low-dimensional latent space with generative capabilities enables efficient structural design through arithmetic operations on latent representations ($\boldsymbol{z}$). However, conditional WGANs cannot map real structures to their latent spaces. To overcome this limitation, we trained an encoder $IG_\psi$ to approximate the inverse mapping $(\boldsymbol{z},\boldsymbol{C})=IG_\psi(\boldsymbol{p})$. This allows derivation of latent representations $\boldsymbol{z}$ from real TPMS structures $\boldsymbol{p}$, facilitating latent space exploration via interpolation or other transformations.

While existing generative models for cellular materials successfully map topology and mechanical properties to latent spaces, they lack explainability in manipulating TPMS unit cell geometry through latent variables or implicit function coefficients. Our proposed inverse TPMS-GAN (ITPMS-GAN) integrates a trained TPMS-GAN: once $\boldsymbol{z}$ is obtained from structure parameters $\boldsymbol{p}$, explicit geometric control can be applied via conditions. In this framework, the encoded latent space $\boldsymbol{z}'$ and edited geometry condition $\bar{\boldsymbol{s}}$ serve as inputs to the generator, producing new TPMS unit cells with parameters $\boldsymbol{p}'$.

We trained $IG_\psi$ post-TPMS-GAN training using both original ($\boldsymbol{p}$) and generated ($\boldsymbol{p}'$) parameters. The reconstruction loss is minimized through:

\begin{equation}
    \mathcal{L}_{IG} = \frac{1}{m}\sum_{i=1}^m\left(\boldsymbol{p}^{(i)}-IG_\psi(\boldsymbol{z}',\bar{\boldsymbol{s}})^{(i)}\right)
\label{eq:21}
\end{equation}

where $m$ denotes batch size (see Table S4). ITPMS-GAN's key advantage is explainable structural editing. Figure \ref{fig:5}\textbf{b} demonstrates pore diameter modification in a test set TPMS unit cell with relative density 0.32 mm, original pore diameter 21 mm, and thickness 14 mm. Mapping $\boldsymbol{p}$ to $\boldsymbol{z}'$ and combining with target diameters (19-23 mm) as input to $G_\phi^2$ (Table S3), we generated structures showing gradual pore variations. Geometric simulations revealed close matches except for 19 mm (18.5 mm actual) and 23 mm (24 mm actual).

The 2D t-SNE plot in Figure \ref{fig:5}c shows the 19 mm structure near training data boundaries, with errors likely from limited training data. The 23/24 mm discrepancy is notable, while structure \textbf{v} forms a distinct D-shape cluster distant from others but similar to structure G. ITPMS-GAN provides explainable TPMS editing beyond latent space interpolation or coefficient adjustment, enabling refined virtual design spaces.

\begin{figure}
    \centering
    \includegraphics[width=1\linewidth]{figures/5.pdf}
    \caption{\textbf{Inversed TPMS-GAN (ITPMS-GAN) and representative examples of edited geometry of TPMS unit cells. a} The implicit function parameters $\boldsymbol{p}$ of TPMS unit cell with geometry features $\boldsymbol{s}$ are encoded into latent vector $\boldsymbol{z}'$ by ITPMS-GAN ($IG_\psi$). Subsequently, the latent representation $\boldsymbol{z}'$ and edited structure parameters $\bar{\boldsymbol{s}}$ are input to generator $G_\phi^2$ for TPMS unit cell construction. \textbf{b} Geometry evolution of TPMS unit cells is demonstrated through pore diameter variation. Red dots indicate designed pore diameters from ITPMS-GAN, while blue dots represent measured values. \textbf{c} 2D t-SNE plot displays implicit function parameters from training data (blue dots) and five designed TPMS unit cells (red stars). A black dashed line traces the structure evolution path in reduced parameter space.}
    \label{fig:5}
\end{figure}

Bone, a cellular material comprising cortical and cancellous components, exhibits elastic modulus ($E$) values spanning 30-30,000 MPa depending on bone mineral density and demographic factors like age, sex, and race \citep{Wang2016}. While capable of self-repair, critical-sized defects require grafting implants for load support and bone regeneration. For TPMS unit cell applications in bio-implants, two optimization targets emerge: (1) matching scaffold $E$ to native bone modulus to mitigate stress shielding and promote recovery \citep{Yang2020}; (2) maximizing yield strength ($\sigma_{ys}$) for structural integrity.

This study employed TPMS-GAN generator $G_\phi^1$ to produce 100,000 TPMS structures, creating virtual design space $\Omega_E$ targeting 6,000 MPa elastic modulus. As shown in Fig. \ref{fig:6}\textbf{e}, random forest model evaluations revealed generated structure moduli ranging 5,400-6,300 MPa, clustering near the target value (red dashed line). To integrate this target into yield strength active learning, we formulated a constraint function quantifying deviation from 6,000 MPa:

\begin{equation}
    c(\boldsymbol{p}') = 1 - \frac{|E(\boldsymbol{p}') - 6000|}{\max(|E(\boldsymbol{p}') - 6000|)}
\label{eq:22}
\end{equation}

Maximized when $E(\boldsymbol{p}') = 6000$, this constraint function application within the virtual design space is visualized in Fig. \ref{fig:6}\textbf{f}.

\begin{figure}
    \centering
    \includegraphics[width=0.75\linewidth]{figures/6.pdf}
    \caption{\textbf{Schematic of constraint-aware active learning strategy. a} Optimal values and uncertainty predictions for constraint-unaware (\textbf{a1}) versus constraint-aware (\textbf{a2}) approaches. \textbf{b} Next query points determined by Expected Improvement (EI, \textbf{b1}) versus constrained EI (\textbf{b2}). \textbf{c} Virtual design space of TPMS unit cells with 6,000 MPa elastic modulus generated by $G_\phi^1$. \textbf{d} Elastic modulus constraint function implementation in virtual design space.}
    \label{fig:6}
\end{figure}

\subsection{Develop high yield strength TPMS unit cells with matched elastic modulus via the constraint-aware strategy}

Cellular material properties depend on both scaffold architecture and constituent materials, characterized by compressive stress-strain curves. Yield strength ($\sigma_{ys}$), defined at 0.2\% strain, quantifies maximum resistance before irreversible deformation. Computational determination proves resource-intensive due to nonlinear plastic behavior and extensive meshing requirements. TPMS unit cell yield strength simulations require approximately 30 minutes per sample, whereas elastic modulus evaluation via finite element homogenization takes roughly 1 minute (computational details in Supplementary Note S6). Bayesian optimization efficiently addresses such expensive black-box problems.

Our constraint-aware active learning approach optimizes yield strength while maintaining elastic modulus targets. A support vector machine (SVM) serves as surrogate model, with bootstrap resampling assessing uncertainties through replacement sampling. Initial implementation sampled 16 candidates from virtual design space for FEM yield strength evaluation. SVM training involved 50 iterations producing resampled training sets and corresponding models. Each initial sample generated 50 predictions used to calculate mean ($\mu$) and standard deviation ($\Sigma$).

Figure \ref{fig:7}c demonstrates constraint-aware Expected Improvement shifting query samples from blue to red dots in the first iteration (Section \ref{sec:2-4}). This transition reflects elastic modulus constraints modifying expected improvement relative to training dataset maxima. Four iterations were conducted, with two samples evaluated per iteration for subsequent feedback into the learning cycle.

The diagonal plot in Fig \ref{fig:7}\textbf{a} demonstrates that model predictions largely align with observed values. The constraint-aware active learning strategy successfully recommends samples exhibiting high yield strength. We track mean square error (MSE) and $R^2$ metrics as the surrogate model undergoes iterative refinement through evaluation of TPMS structures, as shown in Fig \ref{fig:7}\textbf{b}.

The elastic modulus and yield strength distributions of recommended samples are presented in Figs. \ref{fig:7}d-e. Analysis reveals that these samples exhibit elastic moduli clustered near 6,000 MPa, with a mean value of approximately 5,900 MPa – notably higher than the initial dataset's mean of 5,800 MPa. Furthermore, yield strength values for recommended samples consistently exceed those in the initial dataset.

To quantify overall performance $Y$ of TPMS unit cells under the constraint-aware active learning framework, we employ:

\begin{equation}
    Y = Y_E^N + Y_{\sigma_{ys}}^N \label{eq:23}
\end{equation}

where

\begin{equation}
\begin{aligned}
Y_E^N &= \frac{Y_E - \min(Y_E)}{\max(Y_E) - \min(Y_E)}, & Y_E &= \frac{1}{|E(\boldsymbol{p}') - E^*|} \\
Y_{\sigma_{ys}}^N &= \frac{Y_{\sigma_{ys}} - \min(Y_{\sigma_{ys}})}{\max(Y_{\sigma_{ys}}) - \min(Y_{\sigma_{ys}})}
\end{aligned}
\label{eq:24}
\end{equation}

This composite metric effectively quantifies TPMS unit cell performance in achieving scaffold designs with matched elastic modulus and enhanced yield strength. Fig \ref{fig:7}g shows peak performance ($Y$ = 1.72) occurring at iteration 2, significantly surpassing the initial dataset's optimal value (0.22). A transient performance decrease at iteration 3 reflects the active learning process balancing exploration and exploitation strategies, with subsequent recovery to improved performance by iteration 4.

Stress analysis reveals localized concentration at unit cell junctions, as demonstrated in the von Mises stress cloud plot (Fig \ref{fig:7}h) and stress-strain curve (Fig \ref{fig:7}i). The constraint-aware active learning method exhibits extrapolation capability, identifying optimal TPMS structures beyond training data distributions – a critical advantage for clinical applications where patient-specific target properties and initial data variability present challenges.

Implementation of this framework reduces design costs substantially, requiring only 24 yield strength assessments compared to 1,372 evaluations needed for traditional bi-objective generative model training. This efficiency gain translates to an approximately sixfold reduction in design time.

\begin{figure}
    \centering
    \includegraphics[width=1\linewidth]{figures/7.pdf}
    \caption{\textbf{Active learning workflow for yield stress optimization of TPMS unit cells under elastic modulus constraints. a} SVM diagonal plot: recommended structures (red) versus initial data (green). \textbf{b} Iterative improvement of SVM regressor performance. \textbf{c} Query point comparison between EI and constraint-aware EI at iteration 1. \textbf{d} Elastic modulus evolution across iterations. \textbf{e} Yield strength-elastic modulus distributions: recommended samples vs initial data (blue). \textbf{f} Parameter progression through active learning iterations. \textbf{g} Overall performance trajectory. \textbf{h} Stress-strain curves: optimal recommended structure versus initial dataset optimum. \textbf{i} von Mises stress distribution in the recommended optimal structure.}
    \label{fig:7}
\end{figure}

\section{Conclusions}
This study presents a data-efficient, two-stage bi-objective inverse design methodology for TPMS-based orthopedic implants, integrating generative modeling, active learning, and finite element analysis while addressing cost disparities between objectives. The framework simultaneously optimizes:
1) Elastic modulus matching to bone tissue for stress-shielding mitigation
2) Yield strength maximization for mechanical stability

Cubic symmetric TPMS unit cells (G/D) were combined to create isotropic cellular materials, with effective elastic tensors calculated via voxel-based numerical homogenization. Our TPMG-GAN architecture generates target-specific virtual structures through navigator-guided synthesis, while the ITPMS-GAN variant enables explainable geometric feature-to-structure mapping without latent space interpolation or implicit function adjustment. These approaches expand design possibilities for TPMS architectures.

The constraint-aware active learning framework achieved a remarkable performance improvement from 0.2 to 1.7 compared to initial datasets, demonstrating extrapolation capability beyond training data distributions. Combined with sixfold acceleration in design efficiency, this methodology provides robust solutions for clinical scenarios involving variable patient-specific requirements and uncertain mechanical property ranges.

\section*{CRediT authorship contribution statement}
Jiaxuan Ma: Writing – original draft, Software, Methodology, Investigation, Formal analysis, Conceptualization. Bin Cao: Software, Investigation, Conceptualization, Formal analysis. Yuan Tian: Writing – review \& editing, Investigation, Formal analysis. Sheng Sun: Writing – review \& editing, Supervision, Funding acquisition, Formal analysis.

\section*{Declaration of competing interest}
The authors declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix
%% \section{}
%% \label{}
%% If you have bibdatabase file and want bibtex to generate the
%% bibitems, please use
%%
\bibliographystyle{elsarticle-harv} 
\bibliography{refs}
%% else use the following coding to input the bibitems directly in the
%% TeX file.
% \begin{thebibliography}{00}
% %% \bibitem[Author(year)]{label}
% %% Text of bibliographic item
% \bibitem[ ()]{}
% \end{thebibliography}
\end{document}
\endinput
%%
%% End of file `elsarticle-template-harv.tex'.'
